---
title: "Exploratory_Data_Analysis"
author: "Stuart Miller"
date: "July 23, 2019"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r message=FALSE}
# libraries
library(tidyverse)
library(naniar)
library(Hmisc)

# helper files
source('../helper/data_munging.R')
```

# Initial Data Exploration

### Load the data into R

```{r results='hide', message=FALSE}
train <- read_csv('../data/train.csv')
test <- read_csv('../data/test.csv')
```

## Structure of the data

There are 79 features to the data in total. 43 of these features are categorical and 36 of these features are numeric. The training set
consists of 1460 observations and the test set consists of 1459 observations. The training and test sets include an `Id` column, which is not 
a feature of the dataset.

```{r}
# split the training set into numeric and non-numeric sets 
train.numeric <- train %>% select_if(is.numeric)
train.nonnumeric <- train %>% select_if(is.character)

# get the dimensions
print('dimensions of the numeric features (training)')
dim(train.numeric)
print('dimensions of the non-numeric features (training)')
dim(train.nonnumeric)

test.numeric <- test %>% select_if(is.numeric)
test.nonnumeric <- test %>% select_if(is.character)

# get the dimensions
print('dimensions of the numeric features (testing)')
dim(test.numeric)
print('dimensions of the non-numeric features (testing)')
dim(test.nonnumeric)

# Print out the data structure
#str(train)
```

## Missing Data

```{r}
train.nabular <- train %>% bind_shadow()
train.missing.summary <- train.nabular %>% miss_var_summary()
#train.missing.summary

train.missing.summary %>%
  filter(n_miss > 0) %>%
  ggplot(aes(x = reorder(variable, -n_miss), y = pct_miss)) + geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
  labs(title = 'Percent Missing Values of Features (Training Set)',
       y = '% Observations Missing', x = 'Feature Name')

test.nabular <- test %>% bind_shadow()
test.missing.summary <- test.nabular %>% miss_var_summary()
#test.missing.summary

test.missing.summary %>%
  filter(n_miss > 0) %>%
  ggplot(aes(x = reorder(variable, -n_miss), y = pct_miss)) + geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
  labs(title = 'Percent Missing Values of Features (Test Set)',
       y = '% Observations Missing', x = 'Feature Name')
```

**Summary of the Data Missing per Feature from the Datasets**

|Variable       | Number Missing (Train)| Percent Missing (Train)| Number Missing (Test)| Percent Missing (Test)|
|---------------|-----------------------|------------------------|----------------------|------------------------|
|PoolQC         | 1453                  | 99.5%                  | 1456                 | 99.7%                  |
|MiscFeature    | 1406                  | 96.3%                  | 1408                 | 96.5%                  |
|Alley          | 1369                  | 93.7%                  | 1352                 | 92.6%                  |
|Fence          | 1179                  | 80.7%                  | 1169                 | 80.1%                  |
|FireplaceQu    | 690                   | 47.2%                  | 730                  | 50.0%                  |
|LotFrontage    | 259                   | 17.8%                  | 227                  | 15.5%                  |
|GarageType     | 81                    | 5.55%                  | 76                   | 5.21%                  |
|GarageYrBlt    | 81                    | 5.55%                  | 78                   | 5.34%                  |
|GarageFinish   | 81                    | 5.55%                  | 78                   | 5.34%                  |
|GarageQual     | 81                    | 5.55%                  | 78                   | 5.34%                  |
|GarageCond     | 81                    | 5.55%                  | 78                   | 5.34%                  |
|BsmtExposure   | 38                    | 2.60%                  | 44                   | 3.01%                  |
|BsmtFinType2   | 38                    | 2.60%                  | 42                   | 2.87%                  |
|BsmtQual       | 37                    | 2.53%                  | 44                   | 3.01%                  | 
|BsmtCond       | 37                    | 2.53%                  | 45                   | 3.08%                  |
|BsmtFinType1   | 37                    | 2.53%                  | 42                   | 2.87%                  |
|MasVnrType     | 8                     | 0.55%                  | 16                   | 0.27%                  |
|MasVnrArea     | 8                     | 0.55%                  | 15                   | 0.13%                  |
|Electrical     | 1                     | 0.07%                  | N/A                  | N/A                    |
|MSZoning       | N/A                   | N/A                    | 4                    | 0.27%                  |
|Utilities      | N/A                   | N/A                    | 2                    | 0.14%                  |
|BsmtFullBath   | N/A                   | N/A                    | 2                    | 0.14%                  |
|BsmtHalfBath   | N/A                   | N/A                    | 2                    | 0.14%                  |
|Functional     | N/A                   | N/A                    | 2                    | 0.14%                  |
|Exterior1st    | N/A                   | N/A                    | 1                    | 0.07%                  |
|Exterior2nd    | N/A                   | N/A                    | 1                    | 0.07%                  |
|BsmtFinSF1     | N/A                   | N/A                    | 1                    | 0.07%                  |
|BsmtFinSF2     | N/A                   | N/A                    | 1                    | 0.07%                  |
|BsmtUnfSF      | N/A                   | N/A                    | 1                    | 0.07%                  |
|TotalBsmtSF    | N/A                   | N/A                    | 1                    | 0.07%                  |
|KitchenQual    | N/A                   | N/A                    | 1                    | 0.07%                  |
|GarageCars     | N/A                   | N/A                    | 1                    | 0.07%                  |
|GarageArea     | N/A                   | N/A                    | 1                    | 0.07%                  |
|SaleType       | N/A                   | N/A                    | 1                    | 0.07%                  |

**Summary of Missing Data**

5 of the features, `PoolQC`, `MiscFeature`, `Alley`, `Fence`, and `FireplaceQu`, have very high missing rates in both sets of data. It seems unlikely that these features would provide value as imbuing values for the missing values would likely bias the training set towards the imbued value. The feature LotFrontage is missing at a rate of ~17% and ~ 15% in the training and testing set respectively. This is also a fairly high missing rate, but the usefulness of the feature should be investigated. Fortunately, the rate of missingness for each feature is approximately the same between the training and testing datasets.

## Correlation of Numeric Features (Training Set)

```{r}
train.dropna <- train.numeric %>% drop_na() %>% select(-one_of(c('SalePrice')))
res2<-rcorr(as.matrix(train.dropna))
flattenedCor <- flattenCorrMatrix(res2$r, res2$P) %>% arrange(desc(cor))
flattenedCor[1:15,]
```

**Table of Correlated Features from Training Set (r > 0.5)**

|	Feature 1	|	Feature 2	|	Correlation	|
|-----------|-----------|-------------|
|	GarageCars	|	GarageArea	|	0.8394149	|
|	TotalBsmtSF	|	1stFlrSF	|	0.8359994	|
|	GrLivArea	|	TotRmsAbvGrd	|	0.8243121	|
|	YearBuilt	|	GarageYrBlt	|	0.8235195	|
|	2ndFlrSF	|	GrLivArea	|	0.6882916	|
|	BsmtFinSF1	|	BsmtFullBath	|	0.6517267	|
|	BedroomAbvGr	|	TotRmsAbvGrd	|	0.6502846	|
|	YearRemodAdd	|	GarageYrBlt	|	0.6458085	|
|	YearBuilt	|	YearRemodAdd	|	0.6231713	|
|	2ndFlrSF	|	TotRmsAbvGrd	|	0.6177759	|
|	GrLivArea	|	FullBath	|	0.6148873	|
|	OverallQual	|	GrLivArea	|	0.6074661	|
|	2ndFlrSF	|	HalfBath	|	0.6063367	|
|	GarageYrBlt	|	GarageCars	|	0.6009034	|
|	OverallQual	|	GarageCars	|	0.5938029	|
|	GarageYrBlt	|	GarageArea	|	0.5926352	|
|	OverallQual	|	YearBuilt	|	0.5893845	|
|	OverallQual	|	FullBath	|	0.5768747	|
|	OverallQual	|	YearRemodAdd	|	0.5707571	|
|	OverallQual	|	TotalBsmtSF	|	0.5639597	|
|	1stFlrSF	|	GrLivArea	|	0.5613723	|
|	OverallQual	|	GarageYrBlt	|	0.5604251	|
|	OverallQual	|	GarageArea	|	0.5506589	|
|	FullBath	|	TotRmsAbvGrd	|	0.5404489	|
|	YearBuilt	|	GarageCars	|	0.5325628	|
|	BsmtFinSF1	|	TotalBsmtSF	|	0.5309165	|
|	TotalBsmtSF	|	GarageArea	|	0.5220512	|
|	1stFlrSF	|	GarageArea	|	0.521183	|
|	FullBath	|	GarageCars	|	0.520857	|
|	OverallQual	|	1stFlrSF	|	0.5144529	|





