---
title: "Question 2"
author: "Stuart Miller"
date: "August 5, 2019"
output: github_document
---

```{r, echo=T, message=F, warning=FALSE}
library(tidyverse)
library(MASS)
library(caret)
library(knitr)

source('../../helper/visual.R')

load('../../data/data.RData')
```

## Model

"By Hand" constuction.

Based on the correlation heatmap the following parameters have a reasonible correlation with the log of `SalePrice` without high mutual correlation.

* `GarageArea` 
* `OverallQual` 
* `GrLivArea` 
* `TotalBsmtSF` 
* `BsmtQual` 
* `YearRemodAdd` 
* `Fireplaces` 
* `YearBuilt`

Based on EDA, `TotalBsmtSF` varies by `BsmtQual`, so it will be included as an interaction. Year built tend to vary by neighborhood, so neighborhood will be included as an interation on this variable.

This model produces an adjusted R-squared of 0.882, which is an estimate of the variability in logSalePrice that is explained by the model.

```{r, echo=T}
model.formula = log(SalePrice) ~ GarageArea + OverallQual + GrLivArea + TotalBsmtSF:BsmtQual + YearRemodAdd + Fireplaces + YearBuilt:Neighborhood

#model.formula = log(SalePrice) ~ GarageArea + OverallQual + GrLivArea + TotalBsmtSF:BsmtQual + TotalBsmtSF:BsmtExposure + YearRemodAdd + Fireplaces + YearBuilt:Neighborhood + log(LotArea) + TotRmsAbvGrd

m <- lm(model.formula, data = train)
summary(m)
```

## Model Cross Validation

The RMSE and adjusted R-squared are estimated with 10 fold cross validation.

* RMSE: 0.15
* Adj R-squared: 0.86

Since this data is from Kaggle, it was also tested with Kaggle, resulting in a score of 0.15575.

```{r, warning=FALSE}
# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
model.cv <- train(model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)
# print model summary
model.cv
```

## Model Fit Plots

```{r, message=FALSE, warning=FALSE}
basic.fit.plots(train, m)
```




## Prediction

```{r, warning=FALSE}
predictions <- as.double(exp(predict(m, test)))
submission <- data.frame(test$Id,predictions)
names(submission) <- c('Id','SalePrice')
write_csv(submission, '../../data/submission_stuart.csv')
```

