---
title: "Exploratory Data Analysis"
author: "Stuart Miller"
date: "August 2, 2019"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r message=FALSE}
# libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
require(gplots)
require(corrplot)

# helper files
source('../../helper/data_munging.R')
```

# Exploratory Analysis

### Load the data into R

```{r results='hide', message=FALSE}
train <- read_csv('../../data/train.csv')
test <- read_csv('../../data/test.csv')

# add log of saleprice
train <- train %>% mutate(logSalePrice = log(SalePrice))

train$MSSubClass <- factor(train$MSSubClass)
test$MSSubClass <- factor(test$MSSubClass)
```

## Structure of the data

There are 79 features to the data in total. 43 of these features are categorical and 36 of these features are numeric. The training set
consists of 1460 observations and the test set consists of 1459 observations. The training and test sets include an `Id` column, which is not 
a feature of the dataset.

```{r}
# split the training set into numeric and non-numeric sets 
train.numeric <- train %>% select_if(is.numeric)
train.nonnumeric <- train %>% select_if(is.character)

# get the dimensions
print('dimensions of the numeric features (training)')
dim(train.numeric)
print('dimensions of the non-numeric features (training)')
dim(train.nonnumeric)

test.numeric <- test %>% select_if(is.numeric)
test.nonnumeric <- test %>% select_if(is.character)

# get the dimensions
print('dimensions of the numeric features (testing)')
dim(test.numeric)
print('dimensions of the non-numeric features (testing)')
dim(test.nonnumeric)

# Print out the data structure
#str(train)
```





## Univariate and Relation to Response Exploration

### Continuous Variables

#### Distribution of Response Variable

`SalePrice` is the response variable. This is only contained in the training set.

```{r}
ggplot(aes_string(x = 'SalePrice'), data = train) + 
  geom_histogram()
```

#### Correlation of Numeric Features (Training Set)

**Table of Correlated Features from Training Set (r > 0.5)**

```{r}
train.dropna <- train.numeric %>% drop_na() %>% select(-one_of(c('SalePrice')))
res2<-rcorr(as.matrix(train.dropna))
flattenedCor <- flattenCorrMatrix(res2$r, res2$P) %>% arrange(desc(cor))
flattenedCor <- flattenedCor %>% filter(cor > 0.5) %>% select(-one_of(c('p')))
names(flattenedCor) <- c('Feature1','Feature2','Correlation Coefficient')
kable(flattenedCor)
```

**Heatmap of Correlation Amoing Variables**

```{r, fig.height=15, fig.width=15}
heatmap.cor.lab <- function(df){
  df %>%
    keep(is.numeric) %>%
    drop_na() %>%
    cor %>%
    corrplot(addCoef.col = 'white',
             number.digits = 2,
             number.cex = 0.5,
             method = 'square')
}

train %>% heatmap.cor.lab
```


#### Varaince of Explanatory Variables


```{r}
temp.table <- train.numeric %>%
  select(-one_of(c('Id', 'Set'))) %>%
  summarise_all(funs(sd(., na.rm=TRUE))) %>%
  rownames_to_column %>%
  gather(var, value, -rowname) %>%
  arrange(-value) %>%
  select(-one_of(c('rowname')))
names(temp.table) <- c('Feature','Standard Deviation')
kable(temp.table)
```


#### Explanatory Variables

```{r}
# get the names of the continuous variables
cont.names <- names(train.numeric)
print(cont.names)

# add factors for test and train
train.numeric$Set <- rep('train', (dim(train.numeric)[1]))
test.numeric$Set <- rep('test', (dim(test.numeric)[1]))

# combine the training and testing set for histogram plotting
numeric.both <- rbind(train.numeric %>% select(-one_of(c('SalePrice','Id','logSalePrice'))),
                      test.numeric %>% select(-one_of(c('Id'))))
numeric.both$Set <- as.factor(numeric.both$Set)

# remove points based on initial analysis
train.numeric <- train.numeric %>% filter(GrLivArea < 4000)

# add log of sale price
train.numeric <- train.numeric %>% mutate(logSalePrice = log(SalePrice))
```

Based on the plots below, the following features appear to be linearly related to log of sale price:

* `OverallQual`
* `YearBuilt`
* `YearRemodAdd`
* `BsmtFinSF1` - with dummy variable to remove 0s
* `BsmtFinSF2` - with dummy variable to remove 0s
* `BsmtUnfSF` - maybe with a dummy variable
* `TotalBsmtSF` - with dummy variable to remove 0s
* `1stFlrSF`
* `2ndFlrSF` - with dummy variable to remove 0s
* `GrLivArea`
* `FullBath`
* `TotRmsAbvGrd` - somewhat of a curve in the response
* `GarageYrBlt`
* `GarageCars`
* `GarageArea`

The following features may be useful:

`MasVnrArea` - maybe with a dummy variable
`EnclosedPorch` - maybe with a dummy variable

The following features do not seem to have a relationship with log of sale price:

* `LotFrontage`
* `LotArea`
* `OverallCond`
* `LowQualFinSF`
* `BsmtFullBath`
* `BsmtHalfBath`
* `HalfBath`
* `BedroomAbvGr`
* `KitchenAbvGr`
* `Fireplaces`
* `WoodDeckSF`
* `OpenPorchSF`
* `3SsnPorch`
* `PoolArea`
* `ScreenPorch`
* `MiscVal`
* `MoSold`
* `YrSold`

```{r}
ggplot(aes_string(x = 'LotFrontage'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = LotFrontage, y = logSalePrice)) +
  geom_point(alpha = 0.3) + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'LotArea'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = LotArea, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'OverallQual'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = OverallQual, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'OverallCond'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = OverallCond, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'YearBuilt'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = YearBuilt, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'YearRemodAdd'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% ggplot(aes(x = YearRemodAdd, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'MasVnrArea'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(MasVnrArea != 0) %>% ggplot(aes(x = MasVnrArea, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'BsmtFinSF1'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BsmtFinSF1 != 0) %>% ggplot(aes(x = BsmtFinSF1, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'BsmtFinSF2'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BsmtFinSF2 != 0) %>% ggplot(aes(x = BsmtFinSF2, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```


```{r}
ggplot(aes_string(x = 'BsmtUnfSF'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BsmtUnfSF != 0) %>% ggplot(aes(x = BsmtUnfSF, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'TotalBsmtSF'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(TotalBsmtSF != 0) %>% ggplot(aes(x = TotalBsmtSF, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = '`1stFlrSF`'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(`1stFlrSF` != 0) %>% ggplot(aes(x = `1stFlrSF`, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = '`2ndFlrSF`'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(`2ndFlrSF` != 0) %>% ggplot(aes(x = `2ndFlrSF`, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'LowQualFinSF'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(LowQualFinSF != 0) %>% ggplot(aes(x = LowQualFinSF, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'GrLivArea'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(GrLivArea != 0) %>% ggplot(aes(x = GrLivArea, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'BsmtFullBath'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BsmtFullBath != 0) %>% ggplot(aes(x = BsmtFullBath, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'BsmtHalfBath'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BsmtHalfBath != 0) %>% ggplot(aes(x = BsmtHalfBath, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'FullBath'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(FullBath != 0) %>% ggplot(aes(x = FullBath, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```


```{r}
ggplot(aes_string(x = 'HalfBath'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(HalfBath != 0) %>% ggplot(aes(x = HalfBath, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'BedroomAbvGr'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(BedroomAbvGr != 0) %>% ggplot(aes(x = BedroomAbvGr, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'KitchenAbvGr'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(KitchenAbvGr != 0) %>% ggplot(aes(x = KitchenAbvGr, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'TotRmsAbvGrd'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(TotRmsAbvGrd != 0) %>% ggplot(aes(x = TotRmsAbvGrd, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'Fireplaces'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(Fireplaces != 0) %>% ggplot(aes(x = Fireplaces, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```



```{r}
ggplot(aes_string(x = 'GarageYrBlt'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(GarageYrBlt != 0) %>% ggplot(aes(x = GarageYrBlt, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'GarageCars'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(GarageCars != 0) %>% ggplot(aes(x = GarageCars, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'GarageArea'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(GarageArea != 0) %>% ggplot(aes(x = GarageArea, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'WoodDeckSF'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(WoodDeckSF != 0) %>% ggplot(aes(x = WoodDeckSF, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'OpenPorchSF'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(OpenPorchSF != 0) %>% ggplot(aes(x = OpenPorchSF, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'EnclosedPorch'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(EnclosedPorch != 0) %>% ggplot(aes(x = EnclosedPorch, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = '`3SsnPorch`'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(`3SsnPorch` != 0) %>% ggplot(aes(x = `3SsnPorch`, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'ScreenPorch'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(ScreenPorch != 0) %>% ggplot(aes(x = ScreenPorch, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'PoolArea'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(PoolArea != 0) %>% ggplot(aes(x = PoolArea, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'MiscVal'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(MiscVal != 0) %>% ggplot(aes(x = MiscVal, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'MoSold'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(MoSold != 0) %>% ggplot(aes(x = MoSold, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

```{r}
ggplot(aes_string(x = 'YrSold'), data = numeric.both) + 
  geom_histogram() + facet_wrap(~ Set)
train.numeric %>% filter(YrSold != 0) %>% ggplot(aes(x = YrSold, y = logSalePrice)) +
  geom_point() + geom_smooth(method = 'lm')
```

### Categorical Variables

```{r}
# get the names of the continuous variables
cont.names <- names(train.nonnumeric)
print(cont.names)

# add factors for test and train
train.nonnumeric$Set <- rep('train', (dim(train.nonnumeric)[1]))
test.nonnumeric$Set <- rep('test', (dim(test.nonnumeric)[1]))

# combine the training and testing set for histogram plotting
nonnumeric.both <- rbind(train.nonnumeric, test.nonnumeric)
nonnumeric.both$Set <- as.factor(nonnumeric.both$Set)
```

Based on the bar charts below, the following categorical variables should be checked for use in the model:

* MSZoning
* LotShape
* LotConfig
* Neighborhood
* BldgType
* HouseStyle
* RoofStyle
* Exterior1st
* Exterior2nd
* MasVnrType
* ExterQual
* ExterCond
* Foundation
* BsmtQual
* BsmtExposure
* BsmtFinType1
* BsmtFinType2
* CentralAir
* Electrical
* KitchenQual
* FireplaceQu
* GarageType
* GarageFinish
* LandContour - lower interest
* LandSlope - lower interest
* Condition1 - lower interest
* GarageQual - lower interest
* PavedDrive - lower interest
* Fence - with dummy
* SaleType


```{r}
ggplot(aes_string(x = 'MSZoning'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Street'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Alley'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'LotShape'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'LandContour'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Utilities'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'LotConfig'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'LandSlope'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Neighborhood'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Condition1'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = 'Condition2'), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "HouseStyle"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "RoofStyle"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "RoofMatl"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Exterior1st"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Exterior2nd"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "MasVnrType"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "ExterQual"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "ExterCond"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Foundation"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "BsmtQual"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "BsmtExposure"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "BsmtFinType1"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "BsmtFinType2"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Heating"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "HeatingQC"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "CentralAir"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Electrical"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "KitchenQual"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Functional"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "FireplaceQu"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "GarageType"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "GarageFinish"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "GarageQual"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "GarageCond"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "PavedDrive"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "PoolQC"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "Fence"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "MiscFeature"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "SaleType"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

```{r}
ggplot(aes_string(x = "SaleCondition"), data = nonnumeric.both) + 
  geom_bar() + facet_wrap(~ Set)
```

### Continuous and Categorical Variable Interactions

#### Interactions for Garage Variables

A number of varaibles are likely related and could provide useful interactions. The following variables are assocaited with garages.

* Categorical
  * `GarageType`
  * `GarageFinish`
* Continuous
  * `GarageYrBlt`
  * `GarageCars`
  * `GarageArea`

**Correlation between Continupus Garage Features**

As expected, there is a strong correlation betwen area and number of cars (cor ~ 0.83). There is a moderate correlation between size (area and number of cars) and year built (cor ~ 0.57).

```{r}
train %>%
  select(c('GarageArea','GarageCars','GarageYrBlt')) %>%
  drop_na() %>%
  ggpairs()
```


**Interaction Plots for Garage Area**

Plots of log of sale price vs garage area. The slope of log sale price vs garage area does appear to vary by garage finish and garage type (`GarageFinish` and `GarageType`, respectively). This indicates an interaction could be useful.

```{r}
train %>%
  ggplot(aes(x = GarageArea, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageType ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = GarageArea, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageFinish ~ .) +
  geom_smooth(method = 'lm')
```

**Interaction Plots for Garage Cars**

Plots of log of sale price vs number of cars per garage (sizing). The slope of log sale price vs number of cars per garage does appear to vary by garage finish and garage type (`GarageFinish` and `GarageType`, respectively). This indicates an interaction could be useful.

```{r}
train %>%
  ggplot(aes(x = GarageCars, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageType ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = GarageCars, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageFinish ~ .) +
  geom_smooth(method = 'lm')
```

**Interaction Plots for Garage Year Built**

Plots of log of sale price vs garage year built. The slope of log sale price vs garage year built does appear to vary by garage finish and garage type (`GarageFinish` and `GarageType`, respectively). This indicates an interaction could be useful.

```{r}
train %>%
  ggplot(aes(x = GarageYrBlt, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageType ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = GarageYrBlt, y = logSalePrice)) +
  geom_point() + facet_wrap(GarageFinish ~ .) +
  geom_smooth(method = 'lm')
```

#### Interactions for Garage Variables

A number of varaibles are likely related and could provide useful interactions. The following variables are assocaited with garages.

* Categorical
  * `BsmtQual`
  * `BsmtExposure`
  * `BsmtFinType1`
  * `BsmtFinType2`
* Continuous
  * `BsmtFinSF1` - with dummy variable to remove 0s
  * `BsmtFinSF2` - with dummy variable to remove 0s
  * `BsmtUnfSF` - maybe with a dummy variable
  * `TotalBsmtSF` - with dummy variable to remove 0s

**Correlation between Continupus Basement Features**

The continuous basement features do not appear to be closely related.

```{r}
train %>%
  select(c('BsmtFinSF1','BsmtFinSF2','BsmtUnfSF', 'TotalBsmtSF')) %>%
  drop_na() %>%
  ggpairs()
```

**Interaction Plots for BsmtFinSF1**

Plots of BsmtFinSF1 vs log of sale price split on the following factor variables:

* `BsmtQual`
* `BsmtExposure`
* `BsmtFinType1`
* `BsmtFinType2`

Since this is finished basement variable, the unfinised type (`Unf`) is factored out. There does appear to be a relationship between `BsmtFinSF1` (basement finished square feet - first type) and log of sale price.

```{r}
train %>%
  ggplot(aes(x = BsmtFinSF1, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtQual ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = BsmtFinSF1, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtExposure ~ .) +
  geom_smooth(method = 'lm')

train %>%
  filter(!BsmtFinType1 %in% c('Unf')) %>%
  ggplot(aes(x = BsmtFinSF1, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType1 ~ .) +
  geom_smooth(method = 'lm')

train %>% 
  filter(!BsmtFinType2 %in% c('Unf')) %>%
  ggplot(aes(x = BsmtFinSF1, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType2 ~ .) +
  geom_smooth(method = 'lm')
```

**Interaction Plots for BsmtFinSF2**

Plots of BsmtFinSF2 vs log of sale price split on the following factor variables:

* `BsmtQual`
* `BsmtExposure`
* `BsmtFinType1`
* `BsmtFinType2`

Since this is finished basement variable, the unfinised type (`Unf`) is factored out. There does not appear to be a relationship between `BsmtFinSF2` (basement finished square feet - second type) and log of sale price.

```{r}
train %>%
  ggplot(aes(x = BsmtFinSF2, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtQual ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = BsmtFinSF2, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtExposure ~ .) +
  geom_smooth(method = 'lm')

train %>%
  filter(!BsmtFinType1 %in% c('Unf')) %>%
  ggplot(aes(x = BsmtFinSF2, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType1 ~ .) +
  geom_smooth(method = 'lm')

```

**Interaction Plots for BsmtUnfSF**

Plots of BsmtUnfSF vs log of sale price split on the following factor variables:

* `BsmtQual`
* `BsmtExposure`
* `BsmtFinType1`
* `BsmtFinType2`

Since this is an unfinshed basement variable, only the unfinished factor of `BsmtFinType1` and `BsmtFinType2` is considered. There does not appear to be a relationship between `BsmtUnfSF` and log of sale price for `BsmtExposure` and `BsmtFinType1`.

```{r}
train %>%
  ggplot(aes(x = BsmtUnfSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtQual ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = BsmtUnfSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtExposure ~ .) +
  geom_smooth(method = 'lm')

train %>%
  filter(BsmtFinType1 %in% c('Unf')) %>%
  ggplot(aes(x = BsmtUnfSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType1 ~ .) +
  geom_smooth(method = 'lm')

train %>%
  filter(BsmtFinType2 %in% c('Unf')) %>%
  ggplot(aes(x = BsmtUnfSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType2 ~ .) +
  geom_smooth(method = 'lm')
```

**Interaction Plots for TotalBsmtSF**

Plots of TotalBsmtSF vs log of sale price split on the following factor variables:

* `BsmtQual`
* `BsmtExposure`
* `BsmtFinType1`
* `BsmtFinType2`

There does appear to be a relationship between `TotalBsmtSF` (basement square feet) and log of sale price.

```{r}
train %>%
  ggplot(aes(x = TotalBsmtSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtQual ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = TotalBsmtSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtExposure ~ .) +
  geom_smooth(method = 'lm')

train %>%
  ggplot(aes(x = TotalBsmtSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType1 ~ .) +
  geom_smooth(method = 'lm')

train %>% 
  ggplot(aes(x = TotalBsmtSF, y = logSalePrice)) +
  geom_point() + facet_wrap(BsmtFinType2 ~ .) +
  geom_smooth(method = 'lm')
```


