---
title: "Kaggle Project"
author: "Paul Adams"
date: "July 26, 2019"
output: html_document
---

```{r, echo=T, message=F}
library(pacman)
p_load(tidyr,dplyr,purrr,stringr,ggplot2, MASS,DAAG, sjPlot)
```

```{r, echo=F}
setwd("C:/Users/Pablo/Desktop/DS 6371 - Statistical Foundations for Data Science/Kaggle Project")
df <- read.csv("train.csv")
```


```{r, echo=F}

df_ThreeNeighborhoods <- df %>% subset(select = c(SalePrice, Neighborhood, GrLivArea, SaleCondition)) %>%
  filter(Neighborhood %in% c("Edwards", "BrkSide", "NAmes")) %>%
  filter(SaleCondition %in% c("Normal")) %>%
  mutate(logGrLivArea = log(GrLivArea), logSalePrice = log(SalePrice))

colnames(df_ThreeNeighborhoods) <- cbind("SalePrice","Neighborhood","SquareFeet","SaleCondition","logSquareFeet", "logSalePrice")

```

```{r, echo=F}
#refactor with only three levels for neighborhood
df_ThreeNeighborhoods$holder <- as.character(df_ThreeNeighborhoods$Neighborhood)
df_ThreeNeighborhoods$Neighborhood2 <- as.factor(df_ThreeNeighborhoods$holder)
str(df_ThreeNeighborhoods$Neighborhood2)

df_Filtered <- data.frame(df_ThreeNeighborhoods$SalePrice, df_ThreeNeighborhoods$Neighborhood2, df_ThreeNeighborhoods$SquareFeet, df_ThreeNeighborhoods$SaleCondition, df_ThreeNeighborhoods$logSquareFeet, df_ThreeNeighborhoods$logSalePrice)

colnames(df_Filtered) <- cbind("SalePrice","Neighborhood","SquareFeet","SaleCondition","logGrLivArea", "logSalePrice")

df_Edwards <- df_Filtered %>% filter(df_Filtered$Neighborhood == "Edwards") %>% data.frame()
df_NAmes <- df_Filtered %>% filter(df_Filtered$Neighborhood == "NAmes") %>% data.frame()
df_BrkSide <- df_Filtered %>% filter(df_Filtered$Neighborhood == "BrkSide") %>% data.frame()
```

```{r, echo=F}

summary(lm(formula = logSalePrice ~ SquareFeet + Neighborhood + SquareFeet*Neighborhood, data = df_ThreeNeighborhoods))

### start log-transformed data set from df_Filtered
logFeet <- log(df_Filtered$SquareFeet)
df_logFiltered <- data.frame(df_Filtered$SalePrice, df_Filtered$Neighborhood, logFeet)
colnames(df_logFiltered) <- c("SalePrice","Neighborhood","logFeet")

# Build log-log data frame
logPrice <- log(df_Filtered$SalePrice)
df_loglogFiltered <- data.frame(logPrice, df_Filtered$Neighborhood, logFeet)
colnames(df_loglogFiltered) <- c("logPrice","Neighborhood","logFeet")
```
```{r, echo = T}
# Check out residuals for log-linear
ggplot(data = df_Filtered, aes(x = SquareFeet, y = log(SalePrice))) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  theme(
        panel.background = element_rect(fill = 'ivory1')) +
  ggtitle("Log-Linear Data") +
  facet_grid(~Neighborhood)

# Check out residuals for linear-linear
ggplot(data = df_Filtered, aes(x = SquareFeet, y = SalePrice)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  theme(
        panel.background = element_rect(fill = 'ivory1')) +
  ggtitle("Linear-Linear Data") +
  facet_grid(~Neighborhood)
```

### Assumption Checking for Log-Linear
####Based on the output, log-transforming SquareFeet seems necessary:
```{r, echo=F}
summary(lm(SalePrice~SquareFeet, data = df_ThreeNeighborhoods))
par(mfrow=c(2,2))
qqnorm(df_Filtered$SquareFeet, col = "red", main = "Q-Q Plot")
qqline(df_Filtered$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Filtered$SquareFeet), col = "red", main = "Q-Q Plot - Transformed")
qqline(log(df_Filtered$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_Filtered$SquareFeet, col = "red", main = "Histogram")
hist(log(df_Filtered$SquareFeet), col = "red", main = "Histogram - Transformed")
```

### Assumption Checking for Log Sale Price
#### Based on the output, log transforming SalePrice does not seem necessary, but could be helpful:
```{r, echo=F}
par(mfrow=c(2,2))
qqnorm(df_Filtered$SalePrice, col = "red", main = "Q-Q Plot")
qqline(df_Filtered$SalePrice, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Filtered$SalePrice), col = "red", main = "Q-Q Plot - Transformed")
qqline(log(df_Filtered$SalePrice), col = "blue",lwd=2,lty=2)
hist(df_Filtered$SalePrice, col = "red", main = "Histogram")
hist(log(df_Filtered$SalePrice), col = "red", main = "Histogram - Transformed")
```

###Correlation Graphics
```{r, echo=F}
pairs(df_Filtered)
```

### Neighborhood-Level Analysis
```{r, echo=F}
par(mfrow=c(2,2))
qqnorm(df_Edwards$SquareFeet, col = "red", main = "Edwards Q-Q Plot")
qqline(df_Edwards$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Edwards$SquareFeet), col = "red", main = "Edwards Q-Q Plot - Transformed")
qqline(log(df_Edwards$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_Edwards$SquareFeet, col = "red", main = "Edwards Histogram")
hist(log(df_Edwards$SquareFeet), col = "red", main = "Edwards Histogram - Transformed")
```

### Edwards:
```{r, echo=F}
pairs(df_Edwards)
```

```{r,echo=F}
par(mfrow=c(2,2))
qqnorm(df_BrkSide$SquareFeet, col = "red", main = "BrkSide Q-Q Plot")
qqline(df_BrkSide$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_BrkSide$SquareFeet), col = "red", main = "BrkSide Q-Q Plot - Transformed")
qqline(log(df_BrkSide$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_BrkSide$SquareFeet, col = "red", main = "BrkSide Histogram")
hist(log(df_BrkSide$SquareFeet), col = "red", main = "BrkSide Histogram - Transformed")
```

### BrkSide:
```{r,echo=F}
pairs(df_BrkSide)
```

```{r,echo=F}
par(mfrow=c(2,2))
qqnorm(df_NAmes$SquareFeet, col = "red", main = "NAmes Q-Q Plot")
qqline(df_NAmes$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_NAmes$SquareFeet), col = "red", main = "NAmes Q-Q Plot - Transformed")
qqline(log(df_NAmes$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_NAmes$SquareFeet, col = "red", main = "NAmes Histogram")
hist(log(df_NAmes$SquareFeet), col = "red", main = "NAmes Histogram - Transformed")
```

### NAmes
```{r,echo=F}
pairs(df_NAmes)
```

### Linear Models:
#### Based on the output below, there is interaction between Square Footage and the Neighborhood with respect to SalePrice. From the above assumption checking, using a Log-Log model (transform SqFt, but not SalePrice) is necessary. Consequently, I chose to use a log-log model with an interaction term for SqFt*Neighborhood.
```{r, echo=F}
# fit log-log model with interaction terms for SqFt
loglogModelInteract.lm <- lm(logPrice~logFeet + Neighborhood + logFeet*Neighborhood, data = df_loglogFiltered)
colnames(df_loglogFiltered) <- c("logPrice","Neighborhood","logFeet")

plot_model(loglogModelInteract.lm, type = "pred", terms = c("logFeet", "Neighborhood"), title = "Log-Log Model with Interaction")
```


```{r, echo=T}
summary(loglogModelInteract.lm)
confint(loglogModelInteract.lm)
par(mfrow=c(2,2))
plot(loglogModelInteract.lm)
```