---
title: "Kaggle Project"
author: "Paul Adams"
date: "July 26, 2019"
output: html_document
---

```{r, echo=T, message=F}
library(pacman)
p_load(tidyr,dplyr,purrr,stringr,ggplot2, MASS,DAAG, sjPlot, stats)
```

```{r, echo=T}
df <- read.csv('../data/train.csv', stringsAsFactors = F)
dfTest <- read.csv('../data/test.csv', stringsAsFactors = F)
```

### After importing the data, we begain the data cleaning process. First, we isolated the data frame for Edwards, Brookside, and Northwest Ames. With this, we included only "Normal" SaleCondition values since the other types produced outliers.
```{r, echo=T}
df_ThreeNeighborhoods <- df %>%
  mutate(logSalePrice = log(SalePrice)) %>%
  filter(SaleCondition == "Normal") %>%
  subset(select = c(SalePrice, logSalePrice, Neighborhood, GrLivArea)) %>%
  filter(Neighborhood %in% c("Edwards", "BrkSide", "NAmes"))

colnames(df_ThreeNeighborhoods) <- cbind("SalePrice","logSalePrice","Neighborhood","GrLivArea")

```

### Next, we needed to refactor the neighborhoods so that they only contain three levels. Failing to do this could provide issues in downstream analysis. We did this by inserting the Neighborhoods into a holder variable, factoring that, then re-assigning it to a variable that would later be named Neighborhoods, overwriting the previous Neighborhood with more than three levels.
```{r, echo=T}
#refactor with only three levels for neighborhood
df_ThreeNeighborhoods$holder <- as.character(df_ThreeNeighborhoods$Neighborhood)
df_ThreeNeighborhoods$Neighborhood2 <- as.factor(df_ThreeNeighborhoods$holder)
#str(df_ThreeNeighborhoods$Neighborhood2)

df_Filtered <- data.frame(df_ThreeNeighborhoods$SalePrice, df_ThreeNeighborhoods$logSalePrice, df_ThreeNeighborhoods$Neighborhood2, df_ThreeNeighborhoods$GrLivArea)
colnames(df_Filtered) <- cbind("SalePrice","logSalePrice","Neighborhood","GrLivArea")
```


### After this, we re-assigned the three Neighborhood values to indicator (dummy) variables.
```{r, echo=T}
#This turns neighborhoods into indicator (dummy) variables
modelMatrix <- model.matrix(~Neighborhood - 1, data = df_Filtered)

modelData <- data.frame(df_Filtered, modelMatrix)
colnames(modelMatrix)

```


### We knew there is a risk of hurting our model's accuracy by adding more parameters, so we compared the model with and without dummy variables. Because we obtained the same results with both models, we chose to use the model with less parameters as our Full ("Error") model.
```{r, echo=T}
# Neighborhoods as indicator variables
Equal.means.lm.indicators <- lm(logSalePrice~GrLivArea + NeighborhoodNAmes + NeighborhoodBrkSide + NeighborhoodEdwards + NeighborhoodNAmes:GrLivArea + NeighborhoodBrkSide:GrLivArea + NeighborhoodEdwards:GrLivArea, data = modelData)

summary(Equal.means.lm.indicators)
anova(Equal.means.lm.indicators)

# Neighborhoods as levels of factor
Equal.means.lm <- lm(logSalePrice~GrLivArea + Neighborhood + Neighborhood:GrLivArea, data = modelData)

summary(Equal.means.lm)
anova(Equal.means.lm)
```


```{r, echo=T}


df_Edwards <- df_Filtered %>% filter(df_Filtered$Neighborhood == "Edwards") %>% data.frame()
df_NAmes <- df_Filtered %>% filter(df_Filtered$Neighborhood == "NAmes") %>% data.frame()
df_BrkSide <- df_Filtered %>% filter(df_Filtered$Neighborhood == "BrkSide") %>% data.frame()
```

```{r, echo=F}
#This turns neighborhoods into factors
model.matrix(~Neighborhood, data = df)

summary(lm(logSalePrice ~ SquareFeet + Neighborhood + SquareFeet*Neighborhood, data = df_ThreeNeighborhoods))

### start log-transformed data set from df_Filtered
logFeet <- log(df_Filtered$SquareFeet)
df_logFiltered <- data.frame(df_Filtered$SalePrice, df_Filtered$Neighborhood, logFeet)
colnames(df_logFiltered) <- c("SalePrice","Neighborhood","logFeet")

# Build log-log data frame
logPrice <- log(df_Filtered$SalePrice)
df_loglogFiltered <- data.frame(logPrice, df_Filtered$Neighborhood, logFeet)
colnames(df_loglogFiltered) <- c("logPrice","Neighborhood","logFeet")
```
```{r, echo = T}
# Check out residuals for log-linear
ggplot(data = df_Filtered, aes(x = SquareFeet, y = log(SalePrice))) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  theme(
        panel.background = element_rect(fill = 'ivory1')) +
  ggtitle("Log-Linear Data") +
  facet_grid(~Neighborhood)

# Check out residuals for linear-linear
ggplot(data = df_Filtered, aes(x = SquareFeet, y = SalePrice)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  theme(
        panel.background = element_rect(fill = 'ivory1')) +
  ggtitle("Linear-Linear Data") +
  facet_grid(~Neighborhood)
```

### Assumption Checking for Log-Linear
####Based on the output, log-transforming SquareFeet seems necessary:
```{r, echo=F}
summary(lm(SalePrice~SquareFeet, data = df_ThreeNeighborhoods))
par(mfrow=c(2,2))
qqnorm(df_Filtered$SquareFeet, col = "red", main = "Q-Q Plot")
qqline(df_Filtered$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Filtered$SquareFeet), col = "red", main = "Q-Q Plot - Transformed")
qqline(log(df_Filtered$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_Filtered$SquareFeet, col = "red", main = "Histogram")
hist(log(df_Filtered$SquareFeet), col = "red", main = "Histogram - Transformed")
```

### Assumption Checking for Log Sale Price
#### Based on the output, log transforming SalePrice does not seem necessary, but could be helpful:
```{r, echo=F}
par(mfrow=c(2,2))
qqnorm(df_Filtered$SalePrice, col = "red", main = "Q-Q Plot")
qqline(df_Filtered$SalePrice, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Filtered$SalePrice), col = "red", main = "Q-Q Plot - Transformed")
qqline(log(df_Filtered$SalePrice), col = "blue",lwd=2,lty=2)
hist(df_Filtered$SalePrice, col = "red", main = "Histogram")
hist(log(df_Filtered$SalePrice), col = "red", main = "Histogram - Transformed")
```

###Correlation Graphics
```{r, echo=F}
pairs(df_Filtered)
```

### Neighborhood-Level Analysis
```{r, echo=F}
par(mfrow=c(2,2))
qqnorm(df_Edwards$SquareFeet, col = "red", main = "Edwards Q-Q Plot")
qqline(df_Edwards$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_Edwards$SquareFeet), col = "red", main = "Edwards Q-Q Plot - Transformed")
qqline(log(df_Edwards$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_Edwards$SquareFeet, col = "red", main = "Edwards Histogram")
hist(log(df_Edwards$SquareFeet), col = "red", main = "Edwards Histogram - Transformed")
```

### Edwards:
```{r, echo=F}
pairs(df_Edwards)
```

```{r,echo=F}
par(mfrow=c(2,2))
qqnorm(df_BrkSide$SquareFeet, col = "red", main = "BrkSide Q-Q Plot")
qqline(df_BrkSide$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_BrkSide$SquareFeet), col = "red", main = "BrkSide Q-Q Plot - Transformed")
qqline(log(df_BrkSide$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_BrkSide$SquareFeet, col = "red", main = "BrkSide Histogram")
hist(log(df_BrkSide$SquareFeet), col = "red", main = "BrkSide Histogram - Transformed")
```

### BrkSide:
```{r,echo=F}
pairs(df_BrkSide)
```

```{r,echo=F}
par(mfrow=c(2,2))
qqnorm(df_NAmes$SquareFeet, col = "red", main = "NAmes Q-Q Plot")
qqline(df_NAmes$SquareFeet, col = "blue",lwd=2,lty=2)
qqnorm(log(df_NAmes$SquareFeet), col = "red", main = "NAmes Q-Q Plot - Transformed")
qqline(log(df_NAmes$SquareFeet), col = "blue",lwd=2,lty=2)
hist(df_NAmes$SquareFeet, col = "red", main = "NAmes Histogram")
hist(log(df_NAmes$SquareFeet), col = "red", main = "NAmes Histogram - Transformed")
```

### NAmes
```{r,echo=F}
pairs(df_NAmes)
```

### Linear Models:
#### Based on the output below, there is interaction between Square Footage and the Neighborhood with respect to SalePrice. From the above assumption checking, using a Log-Log model (transform SqFt, but not SalePrice) is necessary. Consequently, I chose to use a log-log model with an interaction term for SqFt*Neighborhood.
```{r, echo=F}
# fit log-log model with interaction terms for SqFt
loglogModelInteract.lm <- lm(logPrice~logFeet + Neighborhood + logFeet*Neighborhood, data = df_loglogFiltered)

# fit log-linear model with interaction terms for SqFt
ModelInteract.lm <- lm(logSalePrice~SquareFeet + Neighborhood + SquareFeet*Neighborhood, data = df_Filtered)

PRESS <- function(linear.model){
  pr <- residuals(linear.model)/(1-lm.infulence(linear.model)$hat)
  sum(pr^2)
}

PRESS <- function(linear.model){
  pr <- residuals(linear.model)/(1-lm.influence(linear.model)$hat)
  sum(pr^2)
}

?lm.influence

PRESS(ModelInteract.lm)


colnames(df_loglogFiltered) <- c("logPrice","Neighborhood","logFeet")

plot_model(loglogModelInteract.lm, type = "pred", terms = c("logFeet", "Neighborhood"), title = "Log-Log Model with Interaction")
```

### Begin calculating the extra sum of squares ("Model" aka "Regression")
```{r, echo = T}


# Equal means ("reduced" aka "corrected total") model
Equal.means.lm <- lm(SalePrice~SquareFeet, data = df_Filtered)
anova(Equal.means.lm)

# Full ("separate") model
Separate.means.lm <- lm(SalePrice~GrLivArea + Neighborhood + GrLivArea:Neighborhood, data = df_Filtered)
summary(Separate.means.lm)
anova(Separate.means.lm)

```


```{r, echo=T}
summary(loglogModelInteract.lm)
confint(loglogModelInteract.lm)
par(mfrow=c(2,2))
plot(loglogModelInteract.lm)
```