---
title: "Ames Iowa Housing Prices (Analysis One)"
author: "Chance Robinson"
date: "7/29/2019"
output:
   github_document:
   toc: true
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "../../data/")

```

# ANALYSIS 1:  Requirements

Assume that Century 21 Ames (a real estate company) in Ames Iowa has commissioned you to answer a very important question with respect to their business.  

Century 21 Ames only sells houses in the NAmes, Edwards and BrkSide neighborhoods and would like to simply get an estimate of how the SalePrice of the house is related to the square footage of the living area of the house (GrLIvArea) and if the SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in. 

Build and fit a model that will answer this question, keeping in mind that realtors prefer to talk about living area in increments of 100 sq. ft. Provide your client with the estimate (or estimates if it varies by neighborhood) as well as confidence intervals for any estimate(s) you provide. It turns out that Century 21’s leadership team has a member that has some statistical background. Therefore, make sure and provide evidence that the model assumptions are met and that any suspicious observations (outliers / influential observations) have been identified and addressed. 

Finally, of course, provide your client with a well written conclusion that quantifies the relationship between living area and sale price with respect to these three neighborhoods. Remember that the company is only concerned with the three neighborhoods they sell in.



```{r train 1}
## Multiple Linear Regression

# install.packages("tidyverse")
library(tidyverse)

train <- read.csv("train.csv")

train.filtered <- train %>% 
  subset(select = c(Neighborhood, GrLivArea, SalePrice, SaleCondition)) %>%
  filter(Neighborhood %in% c("Edwards", "BrkSide", "NAmes")) %>%
  filter(SaleCondition %in% c("Normal")) %>%
  mutate(logGrLivArea = log(GrLivArea), logSalePrice = log(SalePrice))
```



## Transformation Analysis

We decided to produce a log of the SalePrice with regards to the other paraemters in the model.  (i.e...a log-linear relationship).  This had the desired effect of normalizing the data, but still left some extreme observations that we felt necessary to handle in order to meet the assumptions of constant variance.  We therefore elected to exclude all but the homes that were in a "normal condition" as it seemed inappropriate to build a model when attempting to predict incomplete observations.


```{r}
# Scatterplot of the data
plot(train.filtered$logSalePrice ~ train.filtered$GrLivArea,xlab="GrLivArea", ylab="logSalePrice")
```



```{r train 2}
head(train.filtered)

# change the reference category
train.filtered$Neighborhood <- relevel(train.filtered$Neighborhood, ref="Edwards")
# table(train.filtered$Neighborhood)

### assumptions ###
# 1)  Normally Distributed
# 2)  Constant Variance
# 3)  Independent Observations

```
```{r fit}
train.fit <- lm(logSalePrice ~ GrLivArea + Neighborhood + GrLivArea * Neighborhood, data = train.filtered)


summary(train.fit)
```

```{r}
ggplot(data = train.fit) +
  geom_point(mapping = aes(x = GrLivArea, y = logSalePrice)) +
  facet_grid(~ Neighborhood)
```



### μ{log(Sales Price)| Living Area, Neighborhood} = β0 + β1(Living Area) + β2(BrkSide) + β3(NAmes) + β4(BrkSide)(Living Area)+ β5(NAmes)(Living Area) 

```{r coeff2}

Intercept = 11.4219
GrLivArea = (exp(0.00051699 * 100) - 1) * 100

NeighborhoodBrkSide = -0.6303
NeighborhoodNAmes = 0.0214

GrLivArea_eNeighborhoodBrkSide = (exp((0.00051699 + 0.00022667) * 100) - 1) * 100
GrLivArea_eNeighborhoodNAmes = (exp((0.00051699 - 0.00016483) * 100) - 1) * 100


Intercept
GrLivArea

NeighborhoodBrkSide
NeighborhoodNAmes

GrLivArea_eNeighborhoodBrkSide
GrLivArea_eNeighborhoodNAmes

```


•	β0 = the y-intercept is 11.05027136 for the reference neighborhood (Edwards) with a Living Area of 0.  (which does not provide any practical value as that would be an extrapolation of the data)

•	**β1 = each additional 100 sq/ ft of the living area added the Edwards neighborhood, holding all other variables constant, would result in a 5.31% multiplicative increase in the median sales price.

•	β2 = the adjustment to the y-intercept for the BrkSide neighborhood is -0.6303.  

•	β3 = the adjustment to the intercept for the NAmes neighborhood is 0.0214

•	**β4 = each additional 100 sq/ ft of the living area added the BrkSide neighborhood, holding all other variables constant, would result in a 7.72% increase in the median sales price.

•	**β5 = each doubling of the living area for the NAmes neighborhood, holding all other variables constant, would result in a 3.58% increase in the median sales price.




## Prediction for a Single Home in the 'BrkSide' neighborhood with a living area of 1500 sq. ft.

```{r confint}
my.pred <- predict(train.fit, data.frame(Neighborhood = 'BrkSide', GrLivArea = 1500))
my.pred.exp <- exp(my.pred)
my.pred.exp
```


```{r confintlog}
confint(train.fit)
```


## 95 Percent confidence intervals for the increase Sales Price for every additional 100 sq/ft

### - 4.15 ~ 6.47% (Edwards)
### - 4.77 ~ 10.45% (BrkSide)
### - 1.15 ~ 6.08% (NAmes)

```{r confintedwards}

edwards_low = (exp(4.067084e-04 * 100) - 1) * 100
edwards_low

edwards_high = (exp(6.272638e-04 * 100) - 1) * 100
edwards_high

```

```{r confintbrkside}

brkside_low = (exp((4.067084e-04 + 5.955141e-05) * 100) - 1) * 100
brkside_low

brkside_high = (exp((6.272638e-04 + 3.937833e-04) * 100) - 1) * 100
brkside_high

```


```{r confintnames}

names_low = (exp((4.067084e-04 - 2.923989e-04) * 100) - 1) * 100
names_low

names_high = (exp((6.272638e-04 - 3.727005e-05) * 100) - 1) * 100
names_high

```


## Residual Plots

The regression lines are broken down by a subset of neighborhoods from the training data set:
```{r plot}
plot(train.fit)
```


## Linear Regression Lines for all three neighborhoods (Log Scale of Sale Price)

```{r plot 2, echo=TRUE}
ggplot(train.fit,aes(y=logSalePrice,x=GrLivArea,color=factor(Neighborhood)))+geom_point()+stat_smooth(method="lm",se=FALSE)
```
