---
title: "Exploratory Data Analysis"
author: "Chance Robinson"
date: "August 4, 2019"
output: 
  github_document:
    toc: true
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r libraries, message=FALSE}
# libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
library(corrr)
library(MASS)
library(caret)

# helper files
source('../../helper/data_munging.R')
```

```{r, cv}
#' Calculates PRESS from `caret` CV model
#'
#' @param model.cv Calculates press from a model 
#' produced by `caret`
#'
PRESS.cv <- function(model.cv) {
  meanN <- 0
  folds <- model.cv$control$index
  for (i in seq(1:length(folds))){
    meanN <- meanN + length(folds[[i]])
  }
  meanN <- meanN / length(folds)
  meanN * ((model.cv$results$RMSE)^2)
}

```



# Exploratory Analysis

### Load the data into R

```{r, load, results='hide', message=FALSE}
train <- read_csv('../../data/train.csv')
test <- read_csv('../../data/test.csv')

```


## Data Cleaning

###  Handle null values for continuous variables
- The `GarageYrBlt (Garage Year Built)` was found to be null when tied rows with an empty Garage Type for all cases of the training data.  It is likely that a Garage Type of NA would represent a property with no garage, and therefore we are setting the `GarageYrBlt` to 0.
- The `LotFrontage` used an impute strategry with the mean value from each data set, as we assumed all houses should have some value for this data point.
- For `MasVnrArea`, we assumed that these properties had no masonry veneer and replaced the NAs with 0.

```{r, numeric_data_cleaning}
# Garage Year Built {"train": 81, "test": 78}

train$GarageYrBlt[is.na(train$GarageYrBlt)] <- 0
test$GarageYrBlt[is.na(test$GarageYrBlt)] <- 0

# Lot Frontage {"train": 259, "test": 227}

train$LotFrontage[is.na(train$LotFrontage)] <- mean(train$LotFrontage, na.rm=TRUE)
test$LotFrontage[is.na(test$LotFrontage)] <- mean(test$LotFrontage, na.rm=TRUE)

# MasVnrArea {"train": 8, "test": 15}
train$MasVnrArea[is.na(train$MasVnrArea)] <- 0
test$MasVnrArea[is.na(test$MasVnrArea)] <- 0

```

```{r, neighborhood}
# Reduce Neighborhood into 3 categories
train %>%
  group_by(Neighborhood) %>%
  summarise(mean = mean(log(SalePrice)), n = n()) %>%
  arrange(desc(mean))


```



###  Handle null values for categorical variables
- Alley 
- MasVnrType
- BsmtQual 
- BsmtCond     
- BsmtExposure
- BsmtFinType1
- BsmtFinType2
- FireplaceQu 
- GarageType
- GarageFinish
- GarageQual
- GarageCond   
- PoolQC 
- Fence
- MiscFeature
- Electrical (SBrkr	Standard Circuit Breakers & Romex)

```{r, non_numeric_data_cleaning, results='hide', echo=FALSE, message=FALSE}


train$Alley[is.na(train$Alley)] <- 'None'
test$Alley[is.na(test$Alley)] <- 'None'

train$MasVnrType[is.na(train$MasVnrType)] <- 'None'
test$MasVnrType[is.na(test$MasVnrType)] <- 'None'

train$BsmtQual[is.na(train$BsmtQual)] <- 'None'
test$BsmtQual[is.na(test$BsmtQual)] <- 'None'

train$BsmtCond[is.na(train$BsmtCond)] <- 'None'
test$BsmtCond[is.na(test$BsmtCond)] <- 'None'

train$BsmtExposure[is.na(train$BsmtExposure)] <- 'None'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'None'

train$BsmtFinType1[is.na(train$BsmtFinType1)] <- 'None'
test$BsmtFinType1[is.na(test$BsmtFinType1)] <- 'None'

train$BsmtFinType2[is.na(train$BsmtFinType2)] <- 'None'
test$BsmtFinType2[is.na(test$BsmtFinType2)] <- 'None'

train$FireplaceQu[is.na(train$FireplaceQu)] <- 'None'
test$FireplaceQu[is.na(test$FireplaceQu)] <- 'None'

train$GarageType[is.na(train$GarageType)] <- 'None'
test$GarageType[is.na(test$GarageType)] <- 'None'

train$GarageFinish[is.na(train$GarageFinish)] <- 'None'
test$GarageFinish[is.na(test$GarageFinish)] <- 'None'

train$GarageQual[is.na(train$GarageQual)] <- 'None'
test$GarageQual[is.na(test$GarageQual)] <- 'None'

train$GarageCond[is.na(train$GarageCond)] <- 'None'
test$GarageCond[is.na(test$GarageCond)] <- 'None'

train$PoolQC[is.na(train$PoolQC)] <- 'None'
test$PoolQC[is.na(test$PoolQC)] <- 'None'

train$Fence[is.na(train$Fence)] <- 'None'
test$Fence[is.na(test$Fence)] <- 'None'

train$MiscFeature[is.na(train$MiscFeature)] <- 'None'
test$MiscFeature[is.na(test$MiscFeature)] <- 'None'

train$Electrical[is.na(train$Electrical)] <- 'SBrkr'
test$Electrical[is.na(test$Electrical)] <- 'SBrkr'

train$BsmtExposure[is.na(train$BsmtExposure)] <- 'None'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'None'

train$Neighborhood <- as.factor(train$Neighborhood)
test$Neighborhood <- as.factor(test$Neighborhood)

train$BldgType <- as.factor(train$BldgType)
test$BldgType <- as.factor(test$BldgType)

train$HouseStyle <- as.factor(train$HouseStyle)
test$HouseStyle <- as.factor(test$HouseStyle)

train$RoofStyle <- as.factor(train$RoofStyle)
test$RoofStyle <- as.factor(test$RoofStyle)

train$RoofMatl <- as.factor(train$RoofMatl)
test$RoofMatl <- as.factor(test$RoofMatl)

train$Exterior1st <- as.factor(train$Exterior1st)
test$Exterior1st <- as.factor(test$Exterior1st)

train$Exterior2nd <- as.factor(train$Exterior2nd)
test$Exterior2nd <- as.factor(test$Exterior2nd)

train$ExterQual <- as.factor(train$ExterQual)
test$ExterQual <- as.factor(test$ExterQual)

train$ExterCond <- as.factor(train$ExterCond)
test$ExterCond <- as.factor(test$ExterCond)

train$Foundation <- as.factor(train$Foundation)
test$Foundation <- as.factor(test$Foundation)

train$Heating <- as.factor(train$Heating)
test$Heating <- as.factor(test$Heating)

train$HeatingQC <- as.factor(train$HeatingQC)
test$HeatingQC <- as.factor(test$HeatingQC)

train$CentralAir <- as.factor(train$CentralAir)
test$CentralAir <- as.factor(test$CentralAir)

train$KitchenQual <- as.factor(train$KitchenQual)
test$KitchenQual <- as.factor(test$KitchenQual)

train$Functional <- as.factor(train$Functional)
test$Functional <- as.factor(test$Functional)

train$PavedDrive <- as.factor(train$PavedDrive)
test$PavedDrive <- as.factor(test$PavedDrive)

train$SaleType <- as.factor(train$SaleType)
test$SaleType <- as.factor(test$SaleType)


train$Utilities <- as.factor(train$Utilities)
test$Utilities <- as.factor(test$Utilities)

```


### set ordinal factors

```{r MSSubClass}
# Reduce Neighborhood into 3 categories
# train %>%
#   group_by(MSSubClass) %>%
#   summarise(mean = mean(log(SalePrice)), n = n()) %>%
#   arrange(mean)


# 1)  Remove Basement Condition as it is highly correlated to Basement Quality
# 2)  Remove Garage Condition as it is highly correlated to Garage Quality
# 3)  Remove utilities from dataframe as it doesn't have enough observations in the 2 levels
train = subset(train, select = -c(Utilities, BsmtCond, GarageCond) )
test = subset(test, select = -c(Utilities, BsmtCond, GarageCond) )


########################################################################################################################################################################


train$MSSubClass <- dplyr::recode(train$MSSubClass, `30` = "30F", `180` = "180F", `45` = "45F", `190` = "190F",
                                  `90` = "190F", `160` = "160F", `50` = "50F", `40` = "40F", `85` = "85F", `70` = "70F",
                                 `80` = "80F", `20` = "20F", `75` = "75F", `120` = "120F", `60` = "60F", `150` = "75F")

test$MSSubClass <- dplyr::recode(test$MSSubClass, `30` = "30F", `180` = "180F", `45` = "45F", `190` = "190F",
                                  `90` = "190F", `160` = "160F", `50` = "50F", `40` = "40F", `85` = "85F", `70` = "70F",
                                 `80` = "80F", `20` = "20F", `75` = "75F", `120` = "120F", `60` = "60F", `150` = "75F")


train$MSSubClass <- as.factor(train$MSSubClass)
test$MSSubClass <- as.factor(test$MSSubClass)


########################################################################################################################################################################
train$GarageQual <- dplyr::recode(train$GarageQual, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
test$GarageQual <- dplyr::recode(test$GarageQual, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)

train$GarageFinish <- dplyr::recode(train$GarageFinish, 'None' = 0, 'Unf' = 1, 'RFn' = 2, 'Fin' = 3)
test$GarageFinish <- dplyr::recode(test$GarageFinish, 'None' = 0, 'Unf' = 1, 'RFn' = 2, 'Fin' = 3)

train$GarageType <- dplyr::recode(train$GarageType, 'None' = 0, 'CarPort' = 1, '2Types' = 2, 'Basment' = 3, 'Detchd' = 4, 'Attchd' = 5, 'BuiltIn' = 6)
test$GarageType <- dplyr::recode(test$GarageType, 'None' = 0, 'CarPort' = 1, '2Types' = 2, 'Basment' = 3, 'Detchd' = 4, 'Attchd' = 5, 'BuiltIn' = 6)


# train$GarageCond <- dplyr::recode(train$GarageCond, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
# test$GarageCond <- dplyr::recode(test$GarageCond, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)

########################################################################################################################################################################


train$BsmtQual <- dplyr::recode(train$BsmtQual, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
test$BsmtQual <- dplyr::recode(test$BsmtQual, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)

# train$BsmtCond <- dplyr::recode(train$BsmtCond, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
# test$BsmtCond <- dplyr::recode(test$BsmtCond, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)


train$BsmtFinType1 <- dplyr::recode(train$BsmtFinType1, 'None' = 0, 'Unf' = 1, 'LwQ' = 2, 'Rec' = 3, 'BLQ' = 4, 'ALQ' = 5, 'GLQ' = 6)
test$BsmtFinType1 <- dplyr::recode(test$BsmtFinType1, 'None' = 0, 'Unf' = 1, 'LwQ' = 2, 'Rec' = 3, 'BLQ' = 4, 'ALQ' = 5, 'GLQ' = 6)


train$BsmtFinType2 <- dplyr::recode(train$BsmtFinType2, 'None' = 0, 'Unf' = 1, 'LwQ' = 2, 'Rec' = 3, 'BLQ' = 4, 'ALQ' = 5, 'GLQ' = 6)
test$BsmtFinType2 <- dplyr::recode(test$BsmtFinType2, 'None' = 0, 'Unf' = 1, 'LwQ' = 2, 'Rec' = 3, 'BLQ' = 4, 'ALQ' = 5, 'GLQ' = 6)


train$BsmtExposure <- dplyr::recode(train$BsmtExposure, 'None' = 0, 'No' = 1, 'Mn' = 2, 'Av' = 3, 'Gd' = 4)
test$BsmtExposure <- dplyr::recode(test$BsmtExposure, 'None' = 0, 'No' = 1, 'Mn' = 2, 'Av' = 3, 'Gd' = 4)

########################################################################################################################################################################

train$LandSlope <- dplyr::recode(train$LandSlope, 'Sev' = 0, 'Mod' = 1, 'Gtl' = 2)
test$LandSlope <- dplyr::recode(test$LandSlope, 'Sev' = 0, 'Mod' = 1, 'Gtl' = 2)


train$MSZoning <- dplyr::recode(train$MSZoning, 'C (all)' = 0, 'RM' = 1, 'RH' = 2, 'RL' = 3, 'FV' = 4)
test$MSZoning <- dplyr::recode(test$MSZoning, 'C (all)' = 0, 'RM' = 1, 'RH' = 2, 'RL' = 3, 'FV' = 4)


train$PoolQC <- dplyr::recode(train$PoolQC, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
test$PoolQC <- dplyr::recode(test$PoolQC, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)


train$FireplaceQu <- dplyr::recode(train$FireplaceQu, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)
test$FireplaceQu <- dplyr::recode(test$FireplaceQu, 'None' = 0, 'Po' = 1, 'Fa' = 2, 'TA' = 3, 'Gd' = 4, 'Ex' = 5)

########################################################################################################################################################################

```




### Set categorical factor variables
```{r non_numeric_factors}


train$Street <- ordered(train$Street, levels = c("Grvl", "Pave"))
test$Street <- ordered(test$Street, levels = c("Grvl", "Pave"))

train$LotShape <- ordered(train$LotShape, levels = c("Reg", "IR1", "IR2", "IR3"))
test$LotShape <- ordered(test$LotShape, levels = c("Reg", "IR1", "IR2", "IR3"))

train$LandContour <- ordered(train$LandContour, levels = c("Bnk", "Lvl", "Low", "HLS"))
test$LandContour <- ordered(test$LandContour, levels = c("Bnk", "Lvl", "Low", "HLS"))

train$LotConfig <- ordered(train$LotConfig, levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"))
test$LotConfig <- ordered(test$LotConfig, levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"))

train$Condition1 <- ordered(train$Condition1, levels = c("Artery", "Feedr", "RRAe", "Norm", "RRAn", "RRNe", "RRNn", "PosA", "PosN"))
test$Condition1 <- ordered(test$Condition1, levels = c("Artery", "Feedr", "RRAe", "Norm", "RRAn", "RRNe", "RRNn", "PosA", "PosN"))

train$Condition2 <- ordered(train$Condition2, levels = c("Artery", "RRNn","RRAn","Feedr", "Norm", "RRAe", "PosN", "PosA"))
test$Condition2 <- ordered(test$Condition2, levels = c("Artery", "RRNn","RRAn","Feedr", "Norm", "RRAe", "PosN", "PosA"))

train$Alley <- ordered(train$Alley, levels = c("None", "Grvl", "Pave"))
test$Alley <- ordered(test$Alley, levels = c("None", "Grvl", "Pave"))

train$MasVnrType <- ordered(train$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))
test$MasVnrType <- ordered(test$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))


train$Fence <- ordered(train$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))
test$Fence <- ordered(test$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))

train$Electrical <- ordered(train$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))
test$Electrical <- ordered(test$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))

train$MiscFeature <- ordered(train$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))
test$MiscFeature <- ordered(test$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))

train$SaleCondition <- factor(train$SaleCondition, levels = c("Abnorml", "AdjLand", "Alloca", "Partial", "Family", "Normal"))
test$SaleCondition <- factor(test$SaleCondition, levels = c("Abnorml", "AdjLand", "Alloca", "Partial", "Family", "Normal"))

train$BldgType[is.na(train$BldgType)] <- '1Fam'
test$BldgType[is.na(test$BldgType)] <- '1Fam'


# str(train)

```




```{r, mssublass_plot}
# EDA for categorical varialbes
train %>% ggplot(aes(x = MSSubClass, y = log(SalePrice))) +
  geom_point() + geom_smooth(method = 'lm')
```


```{r, grlarea_filter}
# remove suspect points from training data
train <- train %>% filter(GrLivArea < 4000)
```



```{r, desribe_training_data}

# describe(train)

```

#### Describe all categorical variables after handling nulls
```{r describe_factors}

# # Scatterplot of Numeric Variable
# train.numeric %>% filter(WoodDeckSF != 0) %>% ggplot(aes(x = WoodDeckSF, y = log(SalePrice))) +
#   geom_point() + geom_smooth(method = 'lm')


# Bar Chart of Categorical Variable
# ggplot(test) + geom_bar(aes(x = Neighborhood))

# Scatterplot of Categroical Variable
# train %>% ggplot(aes(x = Condition2, y = log(SalePrice))) +
#   geom_point() + geom_smooth(method = 'lm')

# Scatterplot of Categroical Variable
# train %>% ggplot(aes(x = Condition2, y = log(SalePrice))) +
#   geom_boxplot()
# 
# ggplot(train,aes(y=log(SalePrice),x=GrLivArea,color=factor(Neighborhood)))+geom_point()+stat_smooth(method="lm",se=FALSE)


# # Scatterplot of Categroical Variable
# train %>% ggplot(aes(x = factor(Neighborhood), y = log(SalePrice))) +
#   geom_boxplot()


# head(train$SalePrice)
# 
# 
# describe(test$Condition2)

```

#### Correlation Table
```{r, salesprice_correlation}
sales.price.cor <- train %>%
  select_if(is.numeric) %>%
  correlate() %>%
  focus(SalePrice)

sales.price.cor %>%
  arrange(desc(SalePrice))
```


### Model Definitions

```{r, model_definition}

# Removals <- c(LotConfig, RoofMat, Heating, PoolArea, MasVnrType, Exterior1st)

custom.model.formula <- log(SalePrice) ~ MSSubClass + MSZoning + LotFrontage + 
    LotArea + Street + Neighborhood + 
    Condition1 + OverallQual + OverallCond + YearBuilt + YearRemodAdd + 
    ExterCond + Foundation + 
    BsmtExposure + BsmtFinType1 + BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + 
    HeatingQC + CentralAir + Electrical + `1stFlrSF` + 
    `2ndFlrSF` + LowQualFinSF + BsmtFullBath + FullBath + HalfBath + 
    KitchenAbvGr + KitchenQual + Functional + FireplaceQu + GarageYrBlt + 
    GarageCars + GarageArea + GarageQual + WoodDeckSF + OpenPorchSF + 
    EnclosedPorch + ScreenPorch + SaleType + SaleCondition

### forward model ###
fwd.model.formula <- log(SalePrice) ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + MSSubClass + OverallCond + YearBuilt + GarageCars + 
    TotalBsmtSF + SaleCondition + LotArea + MSZoning + Functional + 
    CentralAir + KitchenQual + Condition1 + FireplaceQu + BsmtExposure + 
    BsmtFullBath + ScreenPorch + Exterior1st + YearRemodAdd + 
    GarageQual + WoodDeckSF + OpenPorchSF + Street + LotConfig + 
    LotFrontage + Foundation + Heating + KitchenAbvGr + EnclosedPorch + 
    HalfBath + FullBath + MasVnrType + BsmtFinSF2 + HeatingQC + 
    GarageArea + SaleType + ExterCond + PoolArea + BsmtFinType1 + 
    GarageYrBlt + Electrical + `3SsnPorch` + LowQualFinSF

### backward model ###

bkw.model.formula <- log(SalePrice) ~ MSSubClass + MSZoning + LotFrontage +
    LotArea + Street + LotConfig + LandSlope + Neighborhood +
    Condition1 + OverallQual + OverallCond + YearBuilt + YearRemodAdd +
    RoofMatl + Exterior1st + MasVnrType + ExterCond + Foundation +
    BsmtExposure + BsmtFinType1 + BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF +
    Heating + HeatingQC + CentralAir + Electrical + `1stFlrSF` +
    `2ndFlrSF` + LowQualFinSF + BsmtFullBath + FullBath + HalfBath +
    KitchenAbvGr + KitchenQual + Functional + FireplaceQu + GarageYrBlt +
    GarageCars + GarageArea + GarageQual + WoodDeckSF + OpenPorchSF +
    EnclosedPorch + ScreenPorch + PoolArea + SaleType + SaleCondition


### stepwise model ###

stw.model.formula <- log(SalePrice) ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + MSSubClass + OverallCond + YearBuilt + GarageCars + 
    TotalBsmtSF + SaleCondition + LotArea + MSZoning + Functional + 
    CentralAir + KitchenQual + Condition1 + FireplaceQu + BsmtExposure + 
    BsmtFullBath + ScreenPorch + Exterior1st + YearRemodAdd + 
    GarageQual + WoodDeckSF + OpenPorchSF + Street + LotConfig + 
    LotFrontage + Foundation + Heating + KitchenAbvGr + EnclosedPorch + 
    HalfBath + FullBath + MasVnrType + BsmtFinSF2 + HeatingQC + 
    GarageArea + SaleType + ExterCond + PoolArea + BsmtFinType1 + 
    GarageYrBlt + Electrical + `3SsnPorch` + LowQualFinSF


custom.model <- lm(custom.model.formula,
               data = train)


fwd.model <- lm(fwd.model.formula,
               data = train)

bkw.model <- lm(bkw.model.formula,
               data = train)

stw.model <- lm(stw.model.formula,
               data = train)


# Fit the model with all parameters
fit1 <- lm(log(SalePrice) ~ ., data=train)

# Fit the model with only 1 parameter
fit2 <- lm(log(SalePrice) ~ 1, data=train)


```

### Custom Model 

```{r, custom_submit, echo=FALSE, message=FALSE}

test$predicted.log.price <- predict.lm(custom.model, test)
test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
custom_submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))

# write.csv(custom_submit, file = "./cwr_kaggle_submission_custom_model.csv", row.names = FALSE)

summary(custom.model)
```


### Forward Model

```{r, forward_submit, echo=FALSE, message=FALSE}

test$predicted.log.price <- predict.lm(fwd.model, test)
test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
forward_submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))

# write.csv(forward_submit, file = "./cwr_kaggle_submission_forward_model.csv", row.names = FALSE)

summary(fwd.model)
```



### Backward Model

```{r, backward_submit, echo=FALSE, message=FALSE}

test$predicted.log.price <- predict.lm(bkw.model, test)
test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
backward_submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))

# write.csv(backward_submit, file = "./cwr_kaggle_submission_backward_model.csv", row.names = FALSE)

summary(bkw.model)
```


### Stepwise Model

```{r, stepwise_submit, echo=FALSE, message=FALSE}

test$predicted.log.price <- predict.lm(stw.model, test)
test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
stepwise_submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))

# write.csv(stepwise_submit, file = "./cwr_kaggle_submission_stepwise_model.csv", row.names = FALSE)

summary(stw.model)
```


## Cross Validation

### Custom Model CV

```{r, custom_model_cv, message=FALSE, echo=FALSE, warning=FALSE}

# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)

# Train the model
custom.model.cv <- train(custom.model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

custom.model.cv


# get cross-validated PRESS statistic
PCV <- PRESS.cv(custom.model.cv)
PCV

```


### Forward Model CV
```{r, fwd_model_cv, message=FALSE, echo=FALSE, warning=FALSE}


# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)

# Train the model
fwd.model.cv <- train(fwd.model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

fwd.model.cv


# get cross-validated PRESS statistic
PCV <- PRESS.cv(fwd.model.cv)
PCV

```


### Backward Model CV
```{r, bkw_model_cv, message=FALSE, echo=FALSE, warning=FALSE}


# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)

# Train the model
bkw.model.cv <- train(bkw.model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

bkw.model.cv

# get cross-validated PRESS statistic
PCV <- PRESS.cv(bkw.model.cv)
PCV

```

### Stepwise Model CV
```{r, stw_model_cv, message=FALSE, echo=FALSE, warning=FALSE}


# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)

# Train the model
stw.model.cv <- train(stw.model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

stw.model.cv


# get cross-validated PRESS statistic
PCV <- PRESS.cv(stw.model.cv)
PCV


```




```{r, aic_functions, message=F, echo=F, results='hide'}

### AIC functions for different model types

# bwd.model <- stepAIC(fit1,direction="backward")

# fwd.model <- stepAIC(fit2,direction="forward",scope=list(upper=fit1,lower=fit2))

# stw.model <- stepAIC(fit2,direction="both",scope=list(upper=fit1,lower=fit2))

# summary(bwd.model)
# summary(fwd.model)
# summary(stw.model)

```


