---
title: "Exploratory Data Analysis"
author: "Chance Robinson"
date: "August 4, 2019"
output: 
  github_document:
    toc: true
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r message=FALSE}
# libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
# Correlation
library(corrr)
# Forward, Backward and Stepwise Regression
library(MASS)

library(caret)

# helper files
source('../../helper/data_munging.R')
```

# Exploratory Analysis

### Load the data into R

```{r results='hide', message=FALSE}
train <- read_csv('../../data/train.csv')
test <- read_csv('../../data/test.csv')

```




## Data Cleaning

###  Handle null values for continuous variables
- The `GarageYrBlt (Garage Year Built)` was found to be null when tied rows with an empty Garage Type for all cases of the training data.  It is likely that a Garage Type of NA would represent a property with no garage, and therefore we are setting the `GarageYrBlt` to 0.
- The `LotFrontage` used an impute strategry with the mean value from each data set, as we assumed all houses should have some value for this data point.
- For `MasVnrArea`, we assumed that these properties had no masonry veneer and replaced the NAs with 0.

```{r numeric_data_cleaning}
# Garage Year Built {"train": 81, "test": 78}

train$GarageYrBlt[is.na(train$GarageYrBlt)] <- 0
test$GarageYrBlt[is.na(test$GarageYrBlt)] <- 0

# Lot Frontage {"train": 259, "test": 227}

train$LotFrontage[is.na(train$LotFrontage)] <- mean(train$LotFrontage, na.rm=TRUE)
test$LotFrontage[is.na(test$LotFrontage)] <- mean(test$LotFrontage, na.rm=TRUE)


# MasVnrArea {"train": 8, "test": 15}
train$MasVnrArea[is.na(train$MasVnrArea)] <- 0
test$MasVnrArea[is.na(test$MasVnrArea)] <- 0

```

```{r neighborhood}
# Reduce Neighborhood into 3 categories
# train %>% 
#   group_by(Neighborhood) %>%
#   summarise(mean = mean(log(SalePrice)), n = n()) %>%
#   arrange(desc(mean))
# 
# neighborhood_high <- c('NoRidge', 'NridgHt', 'StoneBr', 'Timber', 'Veenker', 'Somerst', 'ClearCr', 'Crawfor', 'Blmngtn', 'CollgCr')
# 
# neighborhood_medium <- c('Gilbert', 'NWAmes', 'SawyerW', 'Mitchel', 'NAmes', 'NPkVill', 'SWISU', 'Blueste', 'Sawyer', 'Edwards')
# 
# neighborhood_low <- c('OldTown', 'BrkSide', 'BrDale', 'MeadowV', 'IDOTRR')
# 
# train$Neighborhood <- case_when(train$Neighborhood %in% c('NoRidge', 'NridgHt', 'StoneBr', 'Timber', 'Veenker', 'Somerst', 'ClearCr', 'Crawfor', 'Blmngtn', 'CollgCr') ~ 'High',
#                train$Neighborhood %in% c('Gilbert', 'NWAmes', 'SawyerW', 'Mitchel', 'NAmes', 'NPkVill', 'SWISU', 'Blueste', 'Sawyer', 'Edwards') ~ 'Medium',
#                train$Neighborhood %in% c('OldTown', 'BrkSide', 'BrDale', 'MeadowV', 'IDOTRR') ~ 'Low')
# 
# 
# test$Neighborhood <- case_when(test$Neighborhood %in% c('NoRidge', 'NridgHt', 'StoneBr', 'Timber', 'Veenker', 'Somerst', 'ClearCr', 'Crawfor', 'Blmngtn', 'CollgCr') ~ 'High',
#                test$Neighborhood %in% c('Gilbert', 'NWAmes', 'SawyerW', 'Mitchel', 'NAmes', 'NPkVill', 'SWISU', 'Blueste', 'Sawyer', 'Edwards') ~ 'Medium',
#                test$Neighborhood %in% c('OldTown', 'BrkSide', 'BrDale', 'MeadowV', 'IDOTRR') ~ 'Low')


table(train$Neighborhood)


```


```{r MSSubClass}
# Reduce Neighborhood into 3 categories
train %>% 
  group_by(MSSubClass) %>%
  summarise(mean = mean(log(SalePrice)), n = n()) %>%
  arrange(desc(mean))

table(train$mean)


```



###  Handle null values for categorical variables
- Alley 
- MasVnrType
- BsmtQual 
- BsmtCond
- BsmtExposure
- BsmtFinType1
- BsmtFinType2
- FireplaceQu 
- GarageType
- GarageFinish
- GarageQual
- GarageCond
- PoolQC 
- Fence
- MiscFeature
- Electrical (SBrkr	Standard Circuit Breakers & Romex)

```{r non_numeric_clean_data, results='hide', echo=FALSE, message=FALSE}


train$Alley[is.na(train$Alley)] <- 'None'
test$Alley[is.na(test$Alley)] <- 'None'

train$MasVnrType[is.na(train$MasVnrType)] <- 'None'
test$MasVnrType[is.na(test$MasVnrType)] <- 'None'

train$BsmtQual[is.na(train$BsmtQual)] <- 'None'
test$BsmtQual[is.na(test$BsmtQual)] <- 'None'

train$BsmtCond[is.na(train$BsmtCond)] <- 'None'
test$BsmtCond[is.na(test$BsmtCond)] <- 'None'

train$BsmtExposure[is.na(train$BsmtExposure)] <- 'None'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'None'

train$BsmtFinType1[is.na(train$BsmtFinType1)] <- 'None'
test$BsmtFinType1[is.na(test$BsmtFinType1)] <- 'None'

train$BsmtFinType2[is.na(train$BsmtFinType2)] <- 'None'
test$BsmtFinType2[is.na(test$BsmtFinType2)] <- 'None'

train$FireplaceQu[is.na(train$FireplaceQu)] <- 'None'
test$FireplaceQu[is.na(test$FireplaceQu)] <- 'None'

train$GarageType[is.na(train$GarageType)] <- 'None'
test$GarageType[is.na(test$GarageType)] <- 'None'

train$GarageFinish[is.na(train$GarageFinish)] <- 'None'
test$GarageFinish[is.na(test$GarageFinish)] <- 'None'

train$GarageQual[is.na(train$GarageQual)] <- 'None'
test$GarageQual[is.na(test$GarageQual)] <- 'None'

train$GarageCond[is.na(train$GarageCond)] <- 'None'
test$GarageCond[is.na(test$GarageCond)] <- 'None'

train$PoolQC[is.na(train$PoolQC)] <- 'None'
test$PoolQC[is.na(test$PoolQC)] <- 'None'

train$Fence[is.na(train$Fence)] <- 'None'
test$Fence[is.na(test$Fence)] <- 'None'

train$MiscFeature[is.na(train$MiscFeature)] <- 'None'
test$MiscFeature[is.na(test$MiscFeature)] <- 'None'

train$Electrical[is.na(train$Electrical)] <- 'SBrkr'
test$Electrical[is.na(test$Electrical)] <- 'SBrkr'

train$BsmtExposure[is.na(train$BsmtExposure)] <- 'None'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'None'


train$Utilities <- as.factor(train$Utilities)
test$Utilities <- as.factor(test$Utilities)





train$BldgType <- as.factor(train$BldgType)
test$BldgType <- as.factor(test$BldgType)

train$HouseStyle <- as.factor(train$HouseStyle)
test$HouseStyle <- as.factor(test$HouseStyle)

train$RoofStyle <- as.factor(train$RoofStyle)
test$RoofStyle <- as.factor(test$RoofStyle)

train$RoofMatl <- as.factor(train$RoofMatl)
test$RoofMatl <- as.factor(test$RoofMatl)

train$Exterior1st <- as.factor(train$Exterior1st)
test$Exterior1st <- as.factor(test$Exterior1st)

train$Exterior2nd <- as.factor(train$Exterior2nd)
test$Exterior2nd <- as.factor(test$Exterior2nd)

train$ExterQual <- as.factor(train$ExterQual)
test$ExterQual <- as.factor(test$ExterQual)

train$ExterCond <- as.factor(train$ExterCond)
test$ExterCond <- as.factor(test$ExterCond)

train$Foundation <- as.factor(train$Foundation)
test$Foundation <- as.factor(test$Foundation)

train$Heating <- as.factor(train$Heating)
test$Heating <- as.factor(test$Heating)

train$HeatingQC <- as.factor(train$HeatingQC)
test$HeatingQC <- as.factor(test$HeatingQC)

train$CentralAir <- as.factor(train$CentralAir)
test$CentralAir <- as.factor(test$CentralAir)

train$KitchenQual <- as.factor(train$KitchenQual)
test$KitchenQual <- as.factor(test$KitchenQual)

train$Functional <- as.factor(train$Functional)
test$Functional <- as.factor(test$Functional)

train$PavedDrive <- as.factor(train$PavedDrive)
test$PavedDrive <- as.factor(test$PavedDrive)

train$SaleType <- as.factor(train$SaleType)
test$SaleType <- as.factor(test$SaleType)

train$BsmtExposure <- as.factor(train$BsmtExposure)
test$BsmtExposure <- as.factor(test$BsmtExposure)


```

### Set ordered factor values
```{r non_numeric_factors}


# train$Neighborhood <- ordered(train$Neighborhood, levels = c("Low", "Medium", "High"))
# test$Neighborhood <- ordered(test$Neighborhood, levels = c("Low", "Medium", "High"))

train$MSZoning <- ordered(train$MSZoning, levels = c("C (all)", "RM", "RH", "RL", "FV"))
test$MSZoning <- ordered(test$MSZoning, levels = c("C (all)", "RM", "RH", "RL", "FV"))

train$Street <- ordered(train$Street, levels = c("Grvl", "Pave"))
test$Street <- ordered(test$Street, levels = c("Grvl", "Pave"))

train$LotShape <- ordered(train$LotShape, levels = c("Reg", "IR1", "IR2", "IR3"))
test$LotShape <- ordered(test$LotShape, levels = c("Reg", "IR1", "IR2", "IR3"))


train$LandContour <- ordered(train$LandContour, levels = c("Bnk", "Lvl", "Low", "HLS"))
test$LandContour <- ordered(test$LandContour, levels = c("Bnk", "Lvl", "Low", "HLS"))

train$LotConfig <- ordered(train$LotConfig, levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"))
test$LotConfig <- ordered(test$LotConfig, levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"))

train$LandSlope <- ordered(train$LandSlope, levels = c("Gtl", "Mod", "Sev"))
test$LandSlope <- ordered(test$LandSlope, levels = c("Gtl", "Mod", "Sev"))


train$Condition1 <- ordered(train$Condition1, levels = c("Artery", "Feedr", "RRAe", "Norm", "RRAn", "RRNe", "RRNn", "PosA", "PosN"))
test$Condition1 <- ordered(test$Condition1, levels = c("Artery", "Feedr", "RRAe", "Norm", "RRAn", "RRNe", "RRNn", "PosA", "PosN"))

train$Condition2 <- ordered(train$Condition2, levels = c("Artery", "RRNn","RRAn","Feedr", "Norm", "RRAe", "PosN", "PosA"))
test$Condition2 <- ordered(test$Condition2, levels = c("Artery", "RRNn","RRAn","Feedr", "Norm", "RRAe", "PosN", "PosA"))

train$Alley <- ordered(train$Alley, levels = c("None", "Grvl", "Pave"))
test$Alley <- ordered(test$Alley, levels = c("None", "Grvl", "Pave"))

train$MasVnrType <- ordered(train$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))
test$MasVnrType <- ordered(test$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))

train$BsmtQual <- ordered(train$BsmtQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$BsmtQual <- ordered(test$BsmtQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$BsmtCond <- ordered(train$BsmtCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$BsmtCond <- ordered(test$BsmtCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

# train$BsmtExposure <- ordered(train$BsmtExposure, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
# test$BsmtExposure <- ordered(test$BsmtExposure, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$BsmtFinType1 <- ordered(train$BsmtFinType1, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))
test$BsmtFinType1 <- ordered(test$BsmtFinType1, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))

train$BsmtFinType2 <- ordered(train$BsmtFinType2, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))
test$BsmtFinType2 <- ordered(test$BsmtFinType2, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))

train$FireplaceQu <- ordered(train$FireplaceQu, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$FireplaceQu <- ordered(test$FireplaceQu, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$GarageType <- ordered(train$GarageType, levels = c("None", "CarPort", "2Types", "Basment", "Detchd", "Attchd", "BuiltIn"))
test$GarageType <- ordered(test$GarageType, levels = c("None", "CarPort", "2Types", "Basment", "Detchd", "Attchd", "BuiltIn"))

train$GarageFinish <- ordered(train$GarageFinish, levels = c("None", "Unf", "RFn", "Fin"))
test$GarageFinish <- ordered(test$GarageFinish, levels = c("None", "Unf", "RFn", "Fin"))

train$GarageQual <- ordered(train$GarageQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$GarageQual <- ordered(test$GarageQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$GarageCond <- ordered(train$GarageCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$GarageCond <- ordered(test$GarageCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$PoolQC <- ordered(train$PoolQC, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$PoolQC <- ordered(test$PoolQC, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$Fence <- ordered(train$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))
test$Fence <- ordered(test$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))

train$Electrical <- ordered(train$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))
test$Electrical <- ordered(test$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))

train$MiscFeature <- ordered(train$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))
test$MiscFeature <- ordered(test$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))


train$SaleCondition <- factor(train$SaleCondition, levels = c("Abnorml", "AdjLand", "Alloca", "Partial", "Family", "Normal"))
test$SaleCondition <- factor(test$SaleCondition, levels = c("Abnorml", "AdjLand", "Alloca", "Partial", "Family", "Normal"))

train$BldgType[is.na(train$BldgType)] <- '1Fam'
test$BldgType[is.na(test$BldgType)] <- '1Fam'


# str(train)

```


```{r}

# describe(train)


```

#### Describe all categorical variables after handling nulls
```{r describe_factors}

# # Scatterplot of Numeric Variable
# train.numeric %>% filter(WoodDeckSF != 0) %>% ggplot(aes(x = WoodDeckSF, y = log(SalePrice))) +
#   geom_point() + geom_smooth(method = 'lm')


# Bar Chart of Categorical Variable
ggplot(test) + geom_bar(aes(x = Neighborhood))

# Scatterplot of Categroical Variable
train %>% ggplot(aes(x = Condition2, y = log(SalePrice))) +
  geom_point() + geom_smooth(method = 'lm')

# Scatterplot of Categroical Variable
train %>% ggplot(aes(x = Condition2, y = log(SalePrice))) +
  geom_boxplot()
# 
# ggplot(train,aes(y=log(SalePrice),x=GrLivArea,color=factor(Neighborhood)))+geom_point()+stat_smooth(method="lm",se=FALSE)


# # Scatterplot of Categroical Variable
# train %>% ggplot(aes(x = factor(Neighborhood), y = log(SalePrice))) +
#   geom_boxplot()


# head(train$SalePrice)
# 
# 
# describe(test$Condition2)

```

#### Correlation Table
```{r}
sales.price.cor <- train %>%
  select_if(is.numeric) %>%
  correlate() %>%
  focus(SalePrice)

sales.price.cor %>%
  arrange(desc(SalePrice))
```


#### base model
```{r model, results='hide', message=FALSE}

# model.formula <- log(SalePrice) ~ OverallQual + GrLivArea + GarageCars + TotalBsmtSF + YearBuilt +YearRemodAdd + Fireplaces + GrLivArea:Neighborhood + as.factor(BldgType)

# model.formula <- log(SalePrice) ~ MSZoning + LotFrontage + LotArea +
#     Street + LotConfig + LandSlope + 
#     Condition2 + BldgType + OverallQual + OverallCond + YearBuilt +
#     YearRemodAdd + RoofMatl + Foundation +
#     BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF +
#     HeatingQC + CentralAir + `1stFlrSF` + `2ndFlrSF` +
#     LowQualFinSF + BsmtFullBath + FullBath + HalfBath + KitchenAbvGr +
#     KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageYrBlt +
#     GarageCars + GarageArea + WoodDeckSF +
#     EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + PoolQC +
#     SaleType + OverallQual:Neighborhood

## forward model ##
# model.formula <- log(SalePrice) ~ OverallQual + Neighborhood + GrLivArea + 
#     BsmtFinType1 + GarageCars + OverallCond + RoofMatl + TotalBsmtSF + 
#     YearBuilt + Condition2 + MSZoning + BsmtUnfSF + SaleCondition + 
#     Functional + BldgType + CentralAir + LotArea + KitchenQual + 
#     ScreenPorch + Condition1 + Fireplaces + Heating + BsmtExposure + 
#     Exterior1st + YearRemodAdd + LandSlope + GarageArea + WoodDeckSF + 
#     LotConfig + Foundation + LotFrontage + HeatingQC + PoolQC + 
#     BsmtFullBath + EnclosedPorch + PoolArea + SaleType + HalfBath + 
#     GarageCond + BsmtQual + FullBath + Street + KitchenAbvGr + 
#     `3SsnPorch` + GarageQual + ExterCond + GarageYrBlt + TotRmsAbvGrd

## backward model ##

# model.formula <- log(SalePrice) ~ MSZoning + LotFrontage + LotArea +
#     Street + LotConfig + LandSlope + Neighborhood + Condition1 +
#     Condition2 + BldgType + OverallQual + OverallCond + YearBuilt +
#     YearRemodAdd + RoofMatl + Exterior1st + ExterCond + Foundation +
#     BsmtQual + BsmtExposure + BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF +
#     Heating + HeatingQC + CentralAir + `1stFlrSF` + `2ndFlrSF` +
#     LowQualFinSF + BsmtFullBath + FullBath + HalfBath + KitchenAbvGr +
#     KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageYrBlt +
#     GarageCars + GarageArea + GarageQual + GarageCond + WoodDeckSF +
#     EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + PoolQC +
#     SaleType + SaleCondition


model.formula <- log(SalePrice) ~ MSZoning + LotFrontage + LotArea + 
    Street + LotConfig + LandSlope + Neighborhood + Condition1 + 
    Condition2 + BldgType + OverallQual + OverallCond + YearBuilt + 
    YearRemodAdd + RoofMatl + Exterior1st + Foundation + BsmtQual + 
    BsmtExposure + BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + Heating + 
    HeatingQC + CentralAir + `1stFlrSF` + `2ndFlrSF` + LowQualFinSF + 
    BsmtFullBath + FullBath + HalfBath + KitchenAbvGr + KitchenQual + 
    Functional + Fireplaces + GarageCars + GarageArea + GarageCond + 
    WoodDeckSF + EnclosedPorch + `3SsnPorch` + ScreenPorch + 
    PoolArea + PoolQC + SaleType + SaleCondition

## stepwise model ##

# model.formula <- log(SalePrice) ~ OverallQual + Neighborhood + GrLivArea + 
#     GarageCars + OverallCond + RoofMatl + TotalBsmtSF + YearBuilt + 
#     Condition2 + MSZoning + BsmtUnfSF + SaleCondition + Functional + 
#     BldgType + CentralAir + LotArea + KitchenQual + ScreenPorch + 
#     Condition1 + Fireplaces + Heating + BsmtExposure + Exterior1st + 
#     YearRemodAdd + LandSlope + GarageArea + WoodDeckSF + LotConfig + 
#     Foundation + LotFrontage + HeatingQC + PoolQC + BsmtFullBath + 
#     EnclosedPorch + PoolArea + SaleType + BsmtFinSF1 + GarageCond + 
#     HalfBath + Street + KitchenAbvGr + FullBath + `3SsnPorch` + 
#     ExterCond + GarageQual


# Remove utilities from dataframe as it doesn't have enough observations in the 2 levels
dat <- subset(train, select = -c(Utilities, Id) )

# dat <- na.omit(dat)

base.model <- lm(model.formula,
               data = train)

fit1 <- lm(log(SalePrice) ~ ., data=dat)

fit2 <- lm(log(SalePrice) ~ 1, data=dat)

# summary(fit1)

```


```{r submit, results='hide', echo=FALSE, message=FALSE}

test$predicted.log.price <- predict.lm(base.model, test)
test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))

# head(submit)

# write.csv(submit, file = "./kaggle_submission.csv", row.names = FALSE)

summary(base.model)
```




```{r aic, message=FALSE, echo=FALSE, results='hide'}
# bwd.model <- stepAIC(fit1,direction="backward")

# fwd.model <- stepAIC(fit2,direction="forward",scope=list(upper=fit1,lower=fit2))

# stpwise.model <- stepAIC(fit2,direction="both",scope=list(upper=fit1,lower=fit2))

# 
# fwd.model$predicted.log.price <- predict.lm(base.model, test)
# 
# stpwise.model$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
# submit <- stpwise.model %>%
#   mutate(SalePrice = exp(predicted.log.price)) %>%
#   subset(select = c(Id, SalePrice))

# write.csv(submit, file = "./kaggle_submission_forward.csv", row.names = FALSE)

# summary(bwd.model)

```

```{r cv, message=FALSE, echo=FALSE}


# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
model.cv <- train(model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

model.cv
```

