---
title: "Exploratory Data Analysis"
author: "Chance Robinson"
date: "August 4, 2019"
output: 
  github_document:
    toc: true
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r message=FALSE}
# libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
# Correlations
library(corrr)
# Stepwise Regression
library(MASS)

library(caret)

# helper files
source('../../helper/data_munging.R')
```

# Exploratory Analysis

### Load the data into R

```{r results='hide', message=FALSE}
train <- read_csv('../../data/train.csv')
test <- read_csv('../../data/test.csv')

train <- train %>% mutate(logSalePrice = log(SalePrice))

```




## Data Cleaning

###  Handle null values for continuous variables
- The `GarageYrBlt (Garage Year Built)` was found to be null when tied rows with an empty Garage Type for all cases of the training data.  It is likely that a Garage Type of NA would represent a property with no garage, and therefore we are setting the `GarageYrBlt` to 0.
- The `LotFrontage` used an impute strategry with the mean value from each data set, as we assumed all houses should have some value for this data point.
- For `MasVnrArea`, we assumed that these properties had no masonry veneer and replaced the NAs with 0.

```{r numeric_data_cleaning}
# Garage Year Built {"train": 81, "test": 78}

train$GarageYrBlt[is.na(train$GarageYrBlt)] <- 0
test$GarageYrBlt[is.na(test$GarageYrBlt)] <- 0

# Lot Frontage {"train": 259, "test": 227}

train$LotFrontage[is.na(train$LotFrontage)] <- mean(train$LotFrontage, na.rm=TRUE)
test$LotFrontage[is.na(test$LotFrontage)] <- mean(test$LotFrontage, na.rm=TRUE)


# MasVnrArea {"train": 8, "test": 15}
train$MasVnrArea[is.na(train$MasVnrArea)] <- 0
test$MasVnrArea[is.na(test$MasVnrArea)] <- 0

```


###  Handle null values for categorical variables
- Alley 
- MasVnrType
- BsmtQual 
- BsmtCond
- BsmtExposure
- BsmtFinType1
- BsmtFinType2
- FireplaceQu 
- GarageType
- GarageFinish
- GarageQual
- GarageCond
- PoolQC 
- Fence
- MiscFeature
- Electrical (SBrkr	Standard Circuit Breakers & Romex)

```{r non_numeric_clean_data}

train$Alley[is.na(train$Alley)] <- 'None'
test$Alley[is.na(test$Alley)] <- 'None'

train$MasVnrType[is.na(train$MasVnrType)] <- 'None'
test$MasVnrType[is.na(test$MasVnrType)] <- 'None'

train$BsmtQual[is.na(train$BsmtQual)] <- 'None'
test$BsmtQual[is.na(test$BsmtQual)] <- 'None'

train$BsmtCond[is.na(train$BsmtCond)] <- 'None'
test$BsmtCond[is.na(test$BsmtCond)] <- 'None'

train$BsmtExposure[is.na(train$BsmtExposure)] <- 'None'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'None'

train$BsmtFinType1[is.na(train$BsmtFinType1)] <- 'None'
test$BsmtFinType1[is.na(test$BsmtFinType1)] <- 'None'

train$BsmtFinType2[is.na(train$BsmtFinType2)] <- 'None'
test$BsmtFinType2[is.na(test$BsmtFinType2)] <- 'None'

train$FireplaceQu[is.na(train$FireplaceQu)] <- 'None'
test$FireplaceQu[is.na(test$FireplaceQu)] <- 'None'

train$GarageType[is.na(train$GarageType)] <- 'None'
test$GarageType[is.na(test$GarageType)] <- 'None'

train$GarageFinish[is.na(train$GarageFinish)] <- 'None'
test$GarageFinish[is.na(test$GarageFinish)] <- 'None'

train$GarageQual[is.na(train$GarageQual)] <- 'None'
test$GarageQual[is.na(test$GarageQual)] <- 'None'

train$GarageCond[is.na(train$GarageCond)] <- 'None'
test$GarageCond[is.na(test$GarageCond)] <- 'None'

train$PoolQC[is.na(train$PoolQC)] <- 'None'
test$PoolQC[is.na(test$PoolQC)] <- 'None'

train$Fence[is.na(train$Fence)] <- 'None'
test$Fence[is.na(test$Fence)] <- 'None'

train$MiscFeature[is.na(train$MiscFeature)] <- 'None'
test$MiscFeature[is.na(test$MiscFeature)] <- 'None'

train$Electrical[is.na(train$Electrical)] <- 'SBrkr'
test$Electrical[is.na(test$Electrical)] <- 'SBrkr'

```

### Set ordered factor values
```{r non_numeric_factors}

train$Alley <- ordered(train$Alley, levels = c("None", "Grvl", "Pave"))
test$Alley <- ordered(test$Alley, levels = c("None", "Grvl", "Pave"))

train$MasVnrType <- ordered(train$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))
test$MasVnrType <- ordered(test$MasVnrType, levels = c("None", "CBlock", "BrkFace", "BrkCmn", "Stone"))

train$BsmtQual <- ordered(train$BsmtQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$BsmtQual <- ordered(test$BsmtQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$BsmtCond <- ordered(train$BsmtCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$BsmtCond <- ordered(test$BsmtCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$BsmtExposure <- ordered(train$BsmtExposure, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$BsmtExposure <- ordered(test$BsmtExposure, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$BsmtFinType1 <- ordered(train$BsmtFinType1, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))
test$BsmtFinType1 <- ordered(test$BsmtFinType1, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))

train$BsmtFinType2 <- ordered(train$BsmtFinType2, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))
test$BsmtFinType2 <- ordered(test$BsmtFinType2, levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"))

train$FireplaceQu <- ordered(train$FireplaceQu, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$FireplaceQu <- ordered(test$FireplaceQu, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$GarageType <- ordered(train$GarageType, levels = c("None", "CarPort", "2Types", "Basment", "Detchd", "Attchd", "BuiltIn"))
test$GarageType <- ordered(test$GarageType, levels = c("None", "CarPort", "2Types", "Basment", "Detchd", "Attchd", "BuiltIn"))

train$GarageFinish <- ordered(train$GarageFinish, levels = c("None", "Unf", "RFn", "Fin"))
test$GarageFinish <- ordered(test$GarageFinish, levels = c("None", "Unf", "RFn", "Fin"))

train$GarageQual <- ordered(train$GarageQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$GarageQual <- ordered(test$GarageQual, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$GarageCond <- ordered(train$GarageCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$GarageCond <- ordered(test$GarageCond, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$PoolQC <- ordered(train$PoolQC, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))
test$PoolQC <- ordered(test$PoolQC, levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"))

train$Fence <- ordered(train$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))
test$Fence <- ordered(test$Fence, levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"))

train$Electrical <- ordered(train$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))
test$Electrical <- ordered(test$Electrical, levels = c("Mix", "FuseP", "FuseF", "FuseA", "SBrkr"))

train$MiscFeature <- ordered(train$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))
test$MiscFeature <- ordered(test$MiscFeature, levels = c("None", "Othr", "Shed", "Gar2", "TenC"))

```

#### Describe all categorical variables after handling nulls
```{r describe_factors}

train.nonnumeric <- train %>% 
  select_if(is.character)

describe(train.nonnumeric)

```

#### Correlation Table
```{r}
sales.price.cor <- train %>%
  select_if(is.numeric) %>%
  correlate() %>%
  focus(SalePrice)

sales.price.cor %>%
  arrange(desc(SalePrice))
```


#### base model
```{r}

model.formula <- log(SalePrice) ~ OverallQual + GrLivArea + GarageArea + TotalBsmtSF + YearBuilt + Neighborhood

base.model <- lm(model.formula,
               data = train)
summary(base.model)

```


```{r cv}


# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
model.cv <- train(model.formula, 
                    data = train,
                    method = 'lm',
                    trControl = train.control)

model.cv
```


```{r submit}
test$predicted.log.price <- predict.lm(base.model, test)

test$predicted.log.price[is.na(test$predicted.log.price)] <- mean(test$predicted.log.price, na.rm=TRUE)
  
submit <- test %>%
  mutate(SalePrice = exp(predicted.log.price)) %>%
  subset(select = c(Id, SalePrice))
head(submit)

# write.csv(submit, file = "./kaggle_submission.csv", row.names = FALSE)
```


